### 2024-04-11 paper/paper.qmd
plots, figures, checks, models

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
library(knitr)
library(marginaleffects)
library(plotly)
library(tibble)
library(margins)
library(kableExtra)
library(arrow)
library(gridExtra)
library(cowplot)
library(lemon)
```

```{r}
ces2020 <-  read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}
```{r}
#| label: tbl-clean-data
#| tbl-cap: "Preview of the cleaned 2020 CES dataset"
#| message: false
#| echo: false

ces2020[1:5, 1:11] |>
  kable()
```

```{r}
#| label: tbl-summary
#| tbl-cap: "Statistics summary of the cleaned 2020 CES dataset"
#| message: false
#| echo: false

ces2020 |>
  summary() |>
  kable()
```

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

I utilized a Bayesian logistic regression model to examine the relationship between voters' political preferences and their media use preferences.The model is formulated as follows:

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i + \beta_4 \times \mbox{CNN}_ + \beta_5 \times \mbox{Fox_News}_ + \beta_6 \times \mbox{MSNBC}_ + \beta_7 \times \mbox{PBS}_ + \beta_8 \times \mbox{Other}_ + \beta_9 \times \mbox{TV_type}_ + \beta_10 \times \mbox{Party}\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
\beta_5 &\sim \mbox{Normal}(0, 2.5) \\
\beta_6 &\sim \mbox{Normal}(0, 2.5) \\
\beta_7 &\sim \mbox{Normal}(0, 2.5) \\
\beta_8 &\sim \mbox{Normal}(0, 2.5) \\
\beta_9 &\sim \mbox{Normal}(0, 2.5) \\
\beta_10 &\sim \mbox{Normal}(0, 2.5)
\end{align}

In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump). The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_10$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively. Media use networks are being represented by the following predictor variables: \text{ABC}_i, \text{CBS}_i, \text{NBC}_i, \text{CNN}_i, \text{Fox_News}_i \text{MSNBC}_i ,\text{PBS}_i, and \text{Other}_i. The rest of the predictor variables are denoted as \text{TV_type}_i and \text{Party}_i, where $i$ indexes the individuals in the dataset.

The intercept and coefficients are assigned informative prior distributions to regularize the model. Specifically, a normal distribution with a mean of 0 and a standard deviation of 2.5 for each parameter is assumed.

This modeling approach is chosen for several reasons. Firstly, logistic regression is well-suited for binary outcome variables, making it appropriate for analyzing voting behavior. Additionally, Bayesian methods enables the incorporation of prior knowledge and uncertainty into our analysis, which provides more robust estimates of the model parameters. Alternative modeling approaches, such as linear regression models, were also considered. However, Bayesian logistic regression is chosen to fit the resulting binary variable of voter's decision.

We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm. We use the default priors from `rstanarm`. Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters. To avoid excessive runtime, we randomly sampled 2500 observations to fit the model. Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see Appendix @sec-model-details).

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

```{r, fig.height = 10, fig.width = 10}

# Create individual plots for each news channel
plot_ABC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(ABC))) +
  geom_bar(position = "dodge") +
  labs(title = "ABC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() +
 # facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_CBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(CBS))) +
  geom_bar(position = "dodge") +
  labs(title = "CBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() +
 # facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_NBC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(NBC))) +
  geom_bar(position = "dodge") +
  labs(title = "NBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() +
 # facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_CNN <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(CNN))) +
  geom_bar(position = "dodge") +
  labs(title = "CNN", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() +
 # facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_Fox_News <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(Fox_News))) +
  geom_bar(position = "dodge") +
  labs(title = "Fox News", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() +
#  facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_MSNBC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(MSNBC))) +
  geom_bar(position = "dodge") +
  labs(title = "MSNBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() +
#  facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_PBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(PBS))) +
  geom_bar(position = "dodge") +
  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal()

plot_Other <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(Other))) +
  geom_bar(position = "dodge") +
  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() +
  guides(fill = FALSE)

legend <- g_legend(plot_PBS + theme(legend.position='bottom'))

grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS + theme(legend.position ='none'), plot_Other, legend, nrow = 3)

```

```{r, fig.height = 6.6, fig.width = 10}

# Create individual plots for each news channel
plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post))) +
  geom_bar(position = "dodge") +
  labs(title = "Posted", x = "Vote", y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_cartesian(ylim = c(0, 4000)) +  
  guides(fill = FALSE)

plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment))) +
  geom_bar(position = "dodge") +
  labs(title = "Commented", x = "Vote", y = "Count") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 4000)) +  
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
 # facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read))) +
  geom_bar(position = "dodge") +
  labs(title = "Read", x = "Vote", y = "Count") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 4000)) +
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
 # facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow))) +
  geom_bar(position = "dodge") +
  labs(title = "Followed", x = "Vote", y = "Count") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 4000)) +
  theme(plot.title = element_text(hjust = 0.5)) +
 # facet_wrap(~ ., ncol = 4) +
  guides(fill = FALSE)

plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward))) +
  geom_bar(position = "dodge") +
  labs(title = "Forwarded", x = "Vote", y = "Count") +
  coord_cartesian(ylim = c(0, 4000)) +
  theme_minimal() +
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5))

legend <- g_legend(plot_forward + theme(legend.position='bottom', 
                                        legend.text = element_text(size = 15, face="bold"), 
                                        legend.title = element_blank()))

grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), legend, nrow = 2)

```

```{r}
# Create individual plots for each news channel
plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post, levels = c("not_selected", "selected")))) +
  geom_bar(position = "stack", stat = "count") +
  labs(title = "Posted", x = "Vote", y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_cartesian(ylim = c(0, 6000)) +  
  guides(fill = FALSE)

plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment, levels = c("not_selected", "selected")))) +
  geom_bar(position = "stack", stat = "count") +
  labs(title = "Commented", x = "Vote", y = "Count") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 6000)) +  
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
  guides(fill = FALSE)

plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read, levels = c("not_selected", "selected")))) +
  geom_bar(position = "stack", stat = "count") +
  labs(title = "Read", x = "Vote", y = "Count") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 6000)) +
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
  guides(fill = FALSE)

plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow, levels = c("not_selected", "selected")))) +
  geom_bar(position = "stack", stat = "count") +
  labs(title = "Followed", x = "Vote", y = "Count") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 6000)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
  guides(fill = FALSE)

plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward, levels = c("not_selected", "selected")))) +
  geom_bar(position = "stack", stat = "count") +
  labs(title = "Forwarded", x = "Vote", y = "Count") +
  coord_cartesian(ylim = c(0, 6000)) +
  theme_minimal() +
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
 # facet_wrap(~ ., ncol = 4) +

#legend <- g_legend(plot_forward + theme(legend.position='bottom', 
                                        #legend.text = element_text(size = 15, face="bold"), 
                                       # legend.title = element_blank())

grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), nrow = 1)

```
```{r}
# Change labels for Fox_News variable
ces2020$Fox_News <- factor(ces2020$Fox_News, labels = c("No", "Yes"))

ggplot(ces2020, aes(x = Fox_News, fill = voted_for)) +
  geom_bar() +
  facet_wrap(facets = vars(Party)) +
  labs(title = "Relationship Between Fox News Consumption and Voting Behavior",
       x = "Fox News",
       y = "Count",
       color = "Voted for Biden (1) or Trump (0)") +
  scale_fill_brewer(palette = "Set1")
 # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
  theme_minimal()
```
```{r}
# Change labels for Fox_News variable
ces2020$CNN <- factor(ces2020$CNN, labels = c("No", "Yes"))

ggplot(ces2020, aes(x = CNN, fill = voted_for)) +
  geom_bar() +
  facet_wrap(facets = vars(Party)) +
  labs(title = "Relationship Between CNN Consumption and Voting Behavior",
       x = "CNN",
       y = "Count",
       color = "Voted for Biden (1) or Trump (0)") +
  scale_fill_brewer(palette = "Set1")
 # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
  theme_minimal()
```

```{r}
ces2020$TV_type <- factor(ces2020$TV_type, labels = c("National & Local", "National"))

scatter_plot <- ggplot(ces2020, aes(x = TV_type, fill = voted_for)) +
  geom_bar() +
  facet_wrap(facets = vars(Party)) +
  labs(title = "Relationship Between TV News Consumption and Voting Behavior",
       x = "TV Type",
       y = "Count",
       color = "Voted for Biden (1) or Trump (0)") +
  scale_fill_brewer(palette = "Set1")
 # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
  theme_minimal()

# Show the plot
scatter_plot

```

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)
political_preferences <-
  readRDS(file = here::here("models/political_preferences.rds"))

```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )
```

```{r}
# Load necessary libraries
library(car)

# Check for multicollinearity using VIF
vif(political_preferences)

# View the model summary
summary(political_preferences)

```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

#pp_check(first_model) +
 # theme_classic() +
 # theme(legend.position = "bottom")

#posterior_vs_prior(first_model) +
  #theme_minimal() +
 # scale_color_brewer(palette = "Set1") +
 # theme(legend.position = "bottom") +
 # coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

#plot(first_model, "trace")

#plot(first_model, "rhat")
```

```{r}
#| label: fig-post_dist
#| fig-cap: Posterior distribution for logistic regression model 
#| echo: false
#| warning: false
#| message: false

pp_check(political_preferences) +
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-post_prior
#| fig-cap: Comparing the posterior with the prior 
#| echo: false
#| warning: false
#| message: false

#### Read data ####
analysis_data1 <- read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))

# Convert variables to factors
#analysis_data$race <- factor(analysis_data$race)
#analysis_data$region <- factor(analysis_data$region)
#analysis_data$employ <- factor(analysis_data$employ)

# Create voted_for variable in binary form
analysis_data1$voted_for_binary <- ifelse(analysis_data1$voted_for == "Biden", 1, 0)

# Model 1 for n = 1000
set.seed(853)

ces2020_reduced <- 
  analysis_data1 |> 
  slice_sample(n = 2500)

posterior_vs_prior(political_preferences, size = 0.3) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  theme(axis.text.x=element_text(hjust=1, vjust=0.5),
        text=element_text(size=8)) +
  coord_flip()
```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-trace1
#| fig-cap: "Trace plot of intercept and race"
#| fig-subcap: ["Trace plot of Intercept", "Trace plot of race White", "Trace plot of race Black", "Trace plot of race Hispanic", "Trace plot of race Middle Eastern", "Trace plot of race Native American", "Trace plot of race Two or more races", "Trace plot of race Other"]
#| layout-ncol: 2

#plot(political_preferences1, "trace")
plot(political_preferences, "trace", "(Intercept)")

plot(political_preferences, "trace", "ABCYes")
plot(political_preferences, "trace", "CBSYes")
plot(political_preferences, "trace", "NBCYes")
plot(political_preferences, "trace", "CNNYes")
plot(political_preferences, "trace", "Fox_NewsYes")
plot(political_preferences, "trace", "MSNBCYes")
plot(political_preferences, "trace", "PBSYes")
plot(political_preferences, "trace", "OtherYes")

```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-trace2
#| fig-cap: "Trace plot of region"
#| fig-subcap: ["Trace plot of region Northeast", "Trace plot of region South", "Trace plot of region West"]
#| layout-ncol: 2

plot(political_preferences, "trace", "TV_typeNational Newscast")
```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-trace3
#| fig-cap: "Trace plot of region"
#| fig-subcap: ["Trace plot of region Northeast", "Trace plot of region South", "Trace plot of region West"]
#| layout-ncol: 2

plot(political_preferences, "trace", "PartyIndependent")
plot(political_preferences, "trace", "PartyOther")
plot(political_preferences, "trace", "PartyRepublican")
```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-rhat
#| fig-cap: "Rhat plot"

plot(political_preferences, "rhat")
```

## Credibility Interval {#sec-credibility-interval}
@fig-modelresults1 shows the 90% credibility interval for the model.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-modelresults1
#| fig-cap: "Credible intervals for predictors of support for Biden"

modelplot(political_preferences, conf_level = 0.90, size = 0.2) +
  labs(x = "90% credibility interval")
```
\newpage

# References

### 2024-04-11 scripts/00-simulate_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Hannah Yu
+# Date: 8 April 2024 
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]

### 2024-04-11 scripts/01-download_data.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from dataverse
+# Author: Hannah Yu
+# Date: 8 April 2024 
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
 
 
 #### Workspace setup ####
@@ -22,15 +21,16 @@ raw_ces2020 <-
   ) 
 
 
+
+
 raw_ces2020 <-
   raw_ces2020 |>
-  select(votereg, CC20_410, CC20_300_1, CC20_300_2, CC20_300_3, CC20_300_4, CC20_300_5, 
-         CC20_300a, CC20_300c, CC20_300b_1, CC20_300b_2, CC20_300b_3, CC20_300b_4, 
-         CC20_300b_5, CC20_300b_6, CC20_300b_7, CC20_300b_8)
+  select(votereg, CC20_410, CC20_300a, CC20_300c, CC20_300b_1, CC20_300b_2, 
+         CC20_300b_3, CC20_300b_4, CC20_300b_5, CC20_300b_6, CC20_300b_7, 
+         CC20_300b_8, CC20_433a)
+
 
 #### Save data in Parquet Format####
-
-#write_csv(the_raw_data, "inputs/data/raw_data.csv") 
 write_parquet(raw_ces2020, "data/raw_data/raw_ces2020.parquet")
               
 

### 2024-04-11 scripts/02-data_cleaning.R

@@ -1,44 +1,88 @@
 #### Preamble ####
 # Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Hannah Yu
+# Date: 8 April 2024 
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 01-download_data.R
+# Any other information needed?  dropped none
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
 
-#### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
+# Read the data and assign it to raw_ces2020
+raw_ces2020 <- read_parquet("data/raw_data/raw_ces2020.parquet", col_types = cols(
+  "votereg" = col_integer(),
+  "CC20_410" = col_integer(),
+  "cc20_300a" = col_integer(),
+  "cc20_300c" = col_integer(),
+  "cc20_300b_1" = col_integer(),
+  "cc20_300b_2" = col_integer(),
+  "cc20_300b_3" = col_integer(),
+  "cc20_300b_4" = col_integer(),
+  "cc20_300b_5" = col_integer(),
+  "cc20_300b_6" = col_integer(),
+  "cc20_300b_7" = col_integer(),
+  "cc20_300b_8" = col_integer(),
+  "CC20_433a" = col_integer()
+))
+
+
+
+
+# only interested in:
+# respondents who are registered to vote: votereg = 1
+# vote for Trump or Biden: CC20_410 = 1 Biden, 2 Trump
+# no NA in independent variables
+
+cleaned_ces2020 <- 
+  raw_ces2020 |>
+  filter(votereg == 1,
+         CC20_410 %in% c(1, 2)) |>
+  filter(!is.na(CC20_433a) &
+           !is.na(CC20_300a) &
+           !is.na(CC20_300b_1) &
+           !is.na(CC20_300b_2) &
[…]

### 2024-04-11 scripts/03-test_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Hannah Yu
+# Date: 8 April 2024 
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]

### 2024-04-11 scripts/04-model.R

@@ -1,37 +1,80 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models
+# Author: Hannah Yu
+# Date: 8 April 2024 
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 01-download_data.R, 02-data_cleaning.R
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
-
+library(testthat)
+library(arrow)
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data1 <- read_parquet("data/analysis_data/cleaned_ces2020.parquet")
 
-### Model data ####
-first_model <-
+
+# Convert variables to factors
+analysis_data1$ABC <- factor(analysis_data1$ABC)
+analysis_data1$CBS <- factor(analysis_data1$CBS)
+analysis_data1$NBC <- factor(analysis_data1$NBC)
+analysis_data1$CNN <- factor(analysis_data1$CNN)
+analysis_data1$Fox_News <- factor(analysis_data1$Fox_News)
+analysis_data1$MSNBC <- factor(analysis_data1$MSNBC)
+analysis_data1$PBS <- factor(analysis_data1$PBS)
+analysis_data1$Other <- factor(analysis_data1$Other)
+analysis_data1$TV_type <- factor(analysis_data1$TV_type)
+#analysis_data1$Newspaper_type <- factor(analysis_data1$Newspaper_type)
+analysis_data1$Party <- factor(analysis_data1$Party)
+
+
+# Create voted_for variable in binary form
+analysis_data1$voted_for_binary <- ifelse(analysis_data1$voted_for == "Biden", 1, 0)
+
+# Model  for n = 2000
+set.seed(853)
+
+ces2020_reduced <- 
+  analysis_data1 |> 
+  slice_sample(n = 2500)
+print(unique(ces2020_reduced$TV_type))
+
+write.csv(ces2020_reduced, file = "reduced_ces2020.csv")
+
+political_preferences <-
   stan_glm(
-    formula = flying_time ~ length + width,
[…]

### 2024-04-11 scripts/05-replications.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Hannah Yu
+# Date: 8 April 2024 
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]

### 2024-04-12 paper/paper.qmd
model, data, results! (whole day of hard work)

@@
 library(margins)
+library(testthat)
 library(kableExtra)
@@
 library(gridExtra)
-library(cowplot)
-library(lemon)
+
+#library(cowplot)
+#library(lemon)
 ```
@@
 ces2020 <-  read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+# change column type to factor
+ces2020 <-
+  ces2020 |>
+  mutate(
+    voted_for = as_factor(voted_for),
+    ABC = as_factor(ABC),
+    CBS = as_factor(CBS),
+    NBC = as_factor(NBC),
+    CNN = as_factor(CNN),
+    Fox_News = as_factor(Fox_News),
+    MSNBC = as_factor(MSNBC),
+    PBS = as_factor(PBS),
+    Other = as_factor(Other),
+    TV_type = factor(
+      TV_type,
+      levels = c(
+        "Local Newscast",
+        "National Newscast",
+        "Both"
+      )
+    ),
+    Party = factor(
+      Party,
+      levels = c(
+        "Democrat",
+        "Republican",
+        "Independent",
+        "Other"
+      )
+    )
+  ) |>
+  select(voted_for, ABC, CBS, NBC, CNN, Fox_News, MSNBC, PBS, Other, TV_type, Party)
 ```
@@
 
+https://onlinelibrary.wiley.com/doi/full/10.1111/j.1467-9477.2011.00284.x
+
 # Data {#sec-data}
+
+Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat] and `kableExtra` [@citeKableExtra].
+
+## Data Source
+
+Data for this research comes from the 2020 Cooperative Election Study (CES) [@citeCes2020], a annual US political survey.
+The CES contains information about Americans' political view, voting behaviours and experiences across various political geography and social context.
+61,000 American adults participated in the survey in 2020.
+
+## Data Cleaning and Variables
+
 ```{r}
@@
 ```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+# change column type to factor
+ces2020 <-
+  ces2020 |>
+  mutate(
+    voted_for = as_factor(voted_for),
+    ABC = as_factor(ABC),
+    CBS = as_factor(CBS),
+    NBC = as_factor(NBC),
+    CNN = as_factor(CNN),
+    Fox_News = as_factor(Fox_News),
+    MSNBC = as_factor(MSNBC),
+    PBS = as_factor(PBS),
+    Other = as_factor(Other),
+    TV_type = factor(
+      TV_type,
+      levels = c(
+        "Local Newscast",
+        "National Newscast",
+        "Both"
+      )
+    ),
+    Party = factor(
+      Party,
+      levels = c(
+        "Democrat",
+        "Republican",
+        "Independent",
+        "Other"
+      )
+    )
+  ) |>
+  select(voted_for, ABC, CBS, NBC, CNN, Fox_News, MSNBC, PBS, Other, TV_type, Party)
+```
+
+Since this paper focuses on analyzing the influence of media usage on registered voters decision, I perform the following data cleaning process and selected the related variables.
+The dataset is cleaned by renaming the column names, changing the variable for from categorical to dummy, selecting the variables of interest, and filtering out missing information and information not related to the study.
+After cleaning, there are 10331 rows of data remain in the cleaned dataset.
+@tbl-clean-data shows a preview of the cleaned dataset.
+
+The dependent variable of my examination is: `presvote20post`, renamed to `voted_for`.
+This variable represents the presidential candidate the respondent voted for in the 2020 election in the form of a numerical variable.
+The variable `votereg` represents whether the respondent is registered to vote using numerical numbers.
+This paper will only analyze respondents who are registered to vote and focus on the outcome of two candidates, Joe Biden representing the Democratic party and Donald Trump representing the Republican party.
+To analyze the observations of interest, I first limited the observations to the ones that responded "Yes" in `votereg`.
+And I filtered the responses in `presvote20post` to only "Biden" or "Trump" and converted the variable into a dummy variable where 1 represents "Biden" and 0 represents "Trump".
+Rest of the variable this paper focuses on are being divided into three categories: Media Use - Networks, Media Use - TV Type, and Party Affiliation.
+
+Media Use - Networks:
+
+-   `CC20_300b_1`, renamed to `ABC`,
+
+    -   This variable reports if the respondent watches ABC.
+A value of 1 signifies that the respondent does watch ABC, while 2 indicates otherwise.
+This variable was converted into a dummy variable, where 1 represents "Yes" and 0 represents "No".
+
+-   `CC20_300b_2`, renamed to `CBS`,
+
+    -   This variable reports if the respondent watches CBS.
+A value of 1 signifies that the respondent does watch CBS, while 2 indicates otherwise.
+This variable was converted into a dummy variable, where 1 represents "Yes" and 0 represents "No".
+
+-   `CC20_300b_3`, renamed to `NBC`; `CC20_300b_4`, renamed to `CNN`; `CC20_300b_5`, renamed to `Fox_News`; `CC20_300b_6`, renamed to `MSNBC`; `CC20_300b_7`, renamed to `PBS`; `CC20_300b_8`, renamed to `Other`,
+
+    -   The interpretation and cleaning process of these variables are the same as `CBS` and `ABC`.
+
+Media Use - TV Type:
+
+-   `CC20_300a`, renamed to `TV_type`,
+
+    -   This variable reports on what kind of TV news the respondent watches. A value of 1 signifies that the respondent watches "Local Newcast", 2 signifies "National Newscast"; 3 "Both".
+
+Party Affiliation:
+
+-   `CC20_433a`, renamed to `Party`,
+
+    -   This variable reports if the respondent political party affiliation.
+A value of 1 signifies that the respondent identifies as "Democrat", 2 signifies "Republican"; 3 "Independent", and 4 "Other".
+
+```{r}
 #| label: tbl-summary
@@
   summary() |>
-  kable()
+  kable() |>
+  kable_styling()
+
 ```
+@tbl-summary presents a summary of the cleaned data, showing detailed statistics about the dataset.
+It is evident that Biden has more supporters in this election.
+The seven listed media networks capture the majority networks people watch; while `Other` captures the rest.
+Due to the small number of respondents that only watch local newscast and missing values associated with this variable, the number of respondents that only watches local newscast becomes 0 after cleaning.
+Therefore, the value "Local Newscast" is excluded from later examinations and modelings.
+There are more respondents identifying as Democrat than than any other party.
+There are almost equal amount of Republicans and Independent voters; and only 534 voters identified as "Other."
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+## Data Measurement
 
-Talk more about it.
+Because the data was collected from surveys, there might be some inconsistencies and misinterpretations of the questions in people's responses.
+Therefore this section disects on what the variables are measuring.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+each of our variable is only representable for the following scenarios.
+
+Firstly, for the variable `votereg` indicating whether a respondent is registered to vote, the variable relies on self-reported information from survey respondents.
+Due to the inefficiencies of the US voter registration system, people who misunderstood their voter registration status might falsely reported their condition.
+For example, some individuals might believe they reached the status simply because they are of age but did not actually register at their local office.
+According to @inaccurate, there are millions of voter registrations that are no longer valid or inaccurate.
+
+Representing the presidential candidate the respondent voted for, `CC20_410` takes into account of recall bias and social desirability bias along with people's reported presidential candidate preference.
+Trump had made many controversial speeches throughout his presidency that contributed to his polarizing image and unpopularity in mainstream media.
+Therefore, many of his voters would conceal their support due to social pressure, potentially leading to under-reporting of votes for Trump in the survey data.
+
+People's media use networks is being represented by if  `ABC`, `CBS`, `NBC`, `CNN`, `Fox_News`, `MSNBC`, `PBS`, and `Other`.
+Relying on people's self-reported preferences, these variables are also subject to recall bias.
+Respondents might overestimate or underestimate their consumptions of certain network based on the content.
+They might only report the network which reported news that left a strong impression on them.
+In addition, respondents might choose to conceal their consumptions of certain media networks due to the network's political affiliation or reputation.
+
+`TV_type` reports the respondents' preference in local newscast or national newscast (or both).
+The main concern over this variable lies in the fact that after data cleaning, the number of respondents exclusively watching local newscasts became zero due to missing values associated with this variable.
+The fact that many missing values are related to this variable could have unobservable implications that require future examinations.
+Therefore this study excludes the effect of only watching local newscast, and centers on people either only consume national newscast or both.
+
+The variable `Party` categories respondents into four categories.
+Only having four categories might overlook the nuanced and diverse political beliefs held by individuals.
+Some may have hybrid or unconventional political views that don't fit neatly into these categories.
+Therefore, their categorization might not accurately describe their party affiliations.
 
@@
 y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
-\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i + \beta_4 \times \mbox{CNN}_ + \beta_5 \times \mbox{Fox_News}_ + \beta_6 \times \mbox{MSNBC}_ + \beta_7 \times \mbox{PBS}_ + \beta_8 \times \mbox{Other}_ + \beta_9 \times \mbox{TV_type}_ + \beta_10 \times \mbox{Party}\\
+\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox_News}_i + \beta_6 \times \mbox{MSNBC}_i + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV_type}_i + \beta_{10} \times \mbox{Party}_i\\
 \alpha &\sim \mbox{Normal}(0, 2.5) \\
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm.
+We run the model in R [@citeR] using the `rstanarm` package of [@citeRstanarm].
 We use the default priors from `rstanarm`.
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+A positive relationship between watching left leaning (Democrat) media networks and voting for Biden; and a similar positive relationship between watching right leaning (Republican) media networks and voting for Trump.
+In particular, according to @grieco2020americans, among the 7 networks identified in this study, Fox News is known as the most conservative media network while CNN and MSNBC stand as leading liberal media.
+Slightly leaning left, ABC, CBS, and NBC are generally neutral.
+PBS is also more liberal and Democratic leaning, but not as extreme as CNN or MSNBC [@blake2014ranking].
+This is assumption is made based on the findings that state exposure to media network would have a influence on voter [@wettstein2017media].
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+As most news and media outlets are more liberal leaning, I expect a slightly higher chance of voting for Biden for voters who watch both local and national newscasts.
+Local newscast might be more be perceived as more trustworthy and more community oriented; therefore, viewers may tend accept content and political opinions from local newscast more easily.
+On the other hand, voters who exclusively watch national news may adopt a more cautious approach and be less inclined to uncritically accept the material presented to them.
+Therefore, voters who watch both local and national newscasts might have a slightly higher chance of supporting Biden.
+
+In terms of the relationship of party affiliation and voting choices.
+There is an easy assumption; the majority of Democrat voters would vote for their candidate Biden, and almost all Republicans voting for Trump.
+I except a even voting outcomes from Independent and Other voters as they have not express their preferences between the two.
+
+In terms of the relationship between party affiliation and voting choices, it's reasonable to expect that the majority of Democrat voters would support their candidate, Biden, while a significant portion of Republican voters would favor Trump.
+This expectation is based on historical voting patterns and the ideological alignment between these parties and their respective candidates.
+However, it's less predictable how Independent and Other voters might vote, as they have not explicitly expressed their preferences between the two main candidates.
+Therefore, I anticipate half of the votes go to Biden and half to Trump.
+
+```{r}
+
+ggplot(ces2020, aes(x = factor(voted_for), fill = PBS)) +
+  geom_bar(position = "dodge") +
+  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
+  theme_minimal()
+```
 
@@
 
+## Data Results
+
 ```{r, fig.height = 10, fig.width = 10}
-
+#| label: fig-network
+#| fig-cap: Distribution of Presidential Preferences by Network
+#| echo: false
+#| warning: false
+#| message: false
+#| 
 # Create individual plots for each news channel
@@
   labs(title = "ABC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() +
- # facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
+  theme_minimal() 
+  #guides(fill = FALSE)
 
@@
   labs(title = "CBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() +
+  theme_minimal() #+
  # facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
+  #guides(fill = FALSE)
 
@@
   labs(title = "NBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() +
+  theme_minimal() #+
  # facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
+  #guides(fill = FALSE)
 
@@
   labs(title = "CNN", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() +
+  theme_minimal() #+
  # facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
+  #guides(fill = FALSE)
 
@@
   labs(title = "Fox News", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() +
+  theme_minimal()# +
 #  facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
+ # guides(fill = FALSE)
 
@@
   labs(title = "MSNBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() +
+  theme_minimal()# +
 #  facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
+  #guides(fill = FALSE)
 
-plot_PBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(PBS))) +
+plot_PBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = PBS)) +
   geom_bar(position = "dodge") +
@@
   geom_bar(position = "dodge") +
-  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() +
-  guides(fill = FALSE)
+  labs(title = "Other", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
+  theme_minimal()# +
+  #guides(fill = FALSE)
 
@@
 
-grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS + theme(legend.position ='none'), plot_Other, legend, nrow = 3)
+grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS, plot_Other, legend, nrow = 3)
+
+#grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS + #theme(legend.position ='none'), plot_Other, legend, nrow = 3)
 
 ```
+```{r, fig.height = 10, fig.width = 10}
+#| label: fig-network
+#| fig-cap: Distribution of Presidential Preferences by Network
+#| echo: false
+#| warning: false
+#| message: false
+# Create individual plots for each news channel
+plot_ABC <- ggplot(ces2020, aes(x = factor(ABC), fill = factor(voted_for))) +
+  geom_bar(position = "dodge") +
+  labs(title = "ABC", x = "ABC", y = "Count") +
+  scale_fill_manual(values = c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+plot_CBS <- ggplot(ces2020, aes(x = factor(CBS), fill = factor(voted_for))) +
+  geom_bar(position = "dodge") +
+  labs(title = "CBS", x = "CBS", y = "Count") +
+  scale_fill_manual(values =  c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+plot_NBC <- ggplot(ces2020, aes(x = factor(NBC), fill = factor(voted_for))) +
+  geom_bar(position = "dodge") +
+  labs(title = "NBC", x = "NBC", y = "Count") +
+  scale_fill_manual(values =  c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+plot_CNN <- ggplot(ces2020, aes(x = factor(CNN), fill = factor(voted_for))) +
+  geom_bar(position = "dodge") +
+  labs(title = "CNN", x = "CNN", y = "Count") +
+  scale_fill_manual(values =  c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+plot_Fox_News <- ggplot(ces2020, aes(x = factor(Fox_News), fill = factor(voted_for))) +
+  geom_bar(position = "dodge") +
+  labs(title = "Fox News", x = "Fox News", y = "Count") +
+  scale_fill_manual(values =  c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+plot_MSNBC <- ggplot(ces2020, aes(x = factor(MSNBC, levels = c("Yes", "No")), fill = factor(voted_for))) +
+  geom_bar(position = "dodge") +
+  labs(title = "MSNBC", x = "MSNBC", y = "Count") +
+  scale_fill_manual(values =  c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+plot_PBS <- ggplot(ces2020, aes(x = factor(PBS, levels = c("Yes", "No")), fill = voted_for)) +
+  geom_bar(position = "dodge") +
+  labs(title = "PBS", x = "PBS", y = "Count") +
+  scale_fill_manual(values =  c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+plot_Other <- ggplot(ces2020, aes(x = factor(Other, levels = c("Yes", "No")), fill = voted_for)) +
+  geom_bar(position = "dodge") +
+  labs(title = "Other", x = "Other", y = "Count") +
+  scale_fill_manual(values = c("blue", "red")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
+  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+
+legend <- g_legend(plot_PBS + theme(legend.position='bottom'))
+
+grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS, plot_Other, legend, nrow = 3)
+
+```
+
+@fig-network depicts the relationship between voters voting preference and media network preference.
+Because more voters voted for Biden, Biden supporters seem to watch more media network overall.
+Therefore, I examine the proportions of voters watching a specific network and voting for one of the two candidates.
+Biden supporters have a higher proportions of watching most networks.
+Among all the networks that have higher proportions of Biden voters, CNN and MSNBC, two of the most Democratic leaning news networks, have a significantly higher proportions of viewers that are Biden supporters and barely any viewers that support Trump.
+The only network that is being consumed by Trump supporters are Fox News, a network know to be Republican leaning.
 
@@
 # Create individual plots for each news channel
-plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Posted", x = "Vote", y = "Count") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5)) +
-  coord_cartesian(ylim = c(0, 4000)) +  
-  guides(fill = FALSE)
-
-plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Commented", x = "Vote", y = "Count") +
-  theme_minimal() +
-  coord_cartesian(ylim = c(0, 4000)) +  
-  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
- # facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
-
-plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Read", x = "Vote", y = "Count") +
-  theme_minimal() +
-  coord_cartesian(ylim = c(0, 4000)) +
-  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
- # facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
-
-plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Followed", x = "Vote", y = "Count") +
-  theme_minimal() +
-  coord_cartesian(ylim = c(0, 4000)) +
-  theme(plot.title = element_text(hjust = 0.5)) +
- # facet_wrap(~ ., ncol = 4) +
-  guides(fill = FALSE)
-
-plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Forwarded", x = "Vote", y = "Count") +
-  coord_cartesian(ylim = c(0, 4000)) +
-  theme_minimal() +
-  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5))
-
-legend <- g_legend(plot_forward + theme(legend.position='bottom', 
-                                        legend.text = element_text(size = 15, face="bold"), 
-                                        legend.title = element_blank()))
-
-grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), legend, nrow = 2)
+# plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post))) +
+#   geom_bar(position = "dodge") +
+#   labs(title = "Posted", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   theme(plot.title = element_text(hjust = 0.5)) +
+#   coord_cartesian(ylim = c(0, 4000)) +  
+#   guides(fill = FALSE)
+# 
+# plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment))) +
+#   geom_bar(position = "dodge") +
+#   labs(title = "Commented", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   coord_cartesian(ylim = c(0, 4000)) +  
+#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
+#  # facet_wrap(~ ., ncol = 4) +
+#   guides(fill = FALSE)
+# 
+# plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read))) +
+#   geom_bar(position = "dodge") +
+#   labs(title = "Read", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   coord_cartesian(ylim = c(0, 4000)) +
+#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
+#  # facet_wrap(~ ., ncol = 4) +
+#   guides(fill = FALSE)
+# 
+# plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow))) +
+#   geom_bar(position = "dodge") +
+#   labs(title = "Followed", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   coord_cartesian(ylim = c(0, 4000)) +
+#   theme(plot.title = element_text(hjust = 0.5)) +
+#  # facet_wrap(~ ., ncol = 4) +
+#   guides(fill = FALSE)
+# 
+# plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward))) +
+#   geom_bar(position = "dodge") +
+#   labs(title = "Forwarded", x = "Vote", y = "Count") +
+#   coord_cartesian(ylim = c(0, 4000)) +
+#   theme_minimal() +
+#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
+# 
+# 
+# legend <- g_legend(plot_forward + theme(legend.position='bottom', 
+#                                         legend.text = element_text(size = 15, face="bold"), 
+#                                         legend.title = element_blank()))
+# 
+# grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), legend, nrow = 2)
 
@@
 # Create individual plots for each news channel
-plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post, levels = c("not_selected", "selected")))) +
-  geom_bar(position = "stack", stat = "count") +
-  labs(title = "Posted", x = "Vote", y = "Count") +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5)) +
-  coord_cartesian(ylim = c(0, 6000)) +  
-  guides(fill = FALSE)
-
-plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment, levels = c("not_selected", "selected")))) +
-  geom_bar(position = "stack", stat = "count") +
-  labs(title = "Commented", x = "Vote", y = "Count") +
-  theme_minimal() +
-  coord_cartesian(ylim = c(0, 6000)) +  
-  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-  guides(fill = FALSE)
-
-plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read, levels = c("not_selected", "selected")))) +
-  geom_bar(position = "stack", stat = "count") +
-  labs(title = "Read", x = "Vote", y = "Count") +
-  theme_minimal() +
-  coord_cartesian(ylim = c(0, 6000)) +
-  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-  guides(fill = FALSE)
-
-plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow, levels = c("not_selected", "selected")))) +
-  geom_bar(position = "stack", stat = "count") +
-  labs(title = "Followed", x = "Vote", y = "Count") +
-  theme_minimal() +
-  coord_cartesian(ylim = c(0, 6000)) +
-  theme(plot.title = element_text(hjust = 0.5)) +
-  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-  guides(fill = FALSE)
-
-plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward, levels = c("not_selected", "selected")))) +
-  geom_bar(position = "stack", stat = "count") +
-  labs(title = "Forwarded", x = "Vote", y = "Count") +
-  coord_cartesian(ylim = c(0, 6000)) +
-  theme_minimal() +
-  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
- # facet_wrap(~ ., ncol = 4) +
-
-#legend <- g_legend(plot_forward + theme(legend.position='bottom', 
-                                        #legend.text = element_text(size = 15, face="bold"), 
-                                       # legend.title = element_blank())
-
-grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), nrow = 1)
+# plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post, levels = c("not_selected", "selected")))) +
+#   geom_bar(position = "stack", stat = "count") +
+#   labs(title = "Posted", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   theme(plot.title = element_text(hjust = 0.5)) +
+#   coord_cartesian(ylim = c(0, 6000)) +  
+#   guides(fill = FALSE)
+# 
+# plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment, levels = c("not_selected", "selected")))) +
+#   geom_bar(position = "stack", stat = "count") +
+#   labs(title = "Commented", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   coord_cartesian(ylim = c(0, 6000)) +  
+#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
+#   guides(fill = FALSE)
+# 
+# plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read, levels = c("not_selected", "selected")))) +
+#   geom_bar(position = "stack", stat = "count") +
+#   labs(title = "Read", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   coord_cartesian(ylim = c(0, 6000)) +
+#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
+#   guides(fill = FALSE)
+# 
+# plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow, levels = c("not_selected", "selected")))) +
+#   geom_bar(position = "stack", stat = "count") +
+#   labs(title = "Followed", x = "Vote", y = "Count") +
+#   theme_minimal() +
+#   coord_cartesian(ylim = c(0, 6000)) +
+#   theme(plot.title = element_text(hjust = 0.5)) +
+#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
+#   guides(fill = FALSE)
+# 
+# plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward, levels = c("not_selected", "selected")))) +
+#   geom_bar(position = "stack", stat = "count") +
+#   labs(title = "Forwarded", x = "Vote", y = "Count") +
+#   coord_cartesian(ylim = c(0, 6000)) +
+#   theme_minimal() +
+#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
+#  # facet_wrap(~ ., ncol = 4) +
+# 
+# 
+# #legend <- g_legend(plot_forward + theme(legend.position='bottom', 
+#                                         #legend.text = element_text(size = 15, face="bold"), 
+#                                        # legend.title = element_blank())
+# 
+# grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), nrow = 1)
 
 ```
+
 ```{r}
+#| label: fig-party
+#| fig-cap: Relationship between TV News Consumption and Voting Behaviour by Party
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(ces2020, aes(x = voted_for, fill = voted_for)) +
+  geom_bar() +
+  facet_wrap(facets = vars(Party)) +
+  labs(title = "Relationship Between Party Affiliation and Voting Behaviour",
+       x = "Vote",
+       y = "Count",
+       color = "Voted for Biden (1) or Trump (0)") +
+  scale_fill_brewer(palette = "Set1")
+
+```
+@fig-party reports on the voting behaviours of voters from different parties.
+Democrat voters mostly voted for Biden, and Republicans for Trump unexpectely.
+The voting outcomes for Independent and Other voters are mostly even, with Biden collecting slightly more votes from the Independent voters.
+
+```{r}
+#| label: fig-foxnews
+#| fig-cap: Relationship between Fox News Consumption and Voting Behaviour by Party
+#| echo: false
+#| warning: false
+#| message: false
+
 # Change labels for Fox_News variable
-ces2020$Fox_News <- factor(ces2020$Fox_News, labels = c("No", "Yes"))
+#ces2020$Fox_News <- factor(ces2020$Fox_News, labels = c("No", "Yes"))
 
@@
   facet_wrap(facets = vars(Party)) +
-  labs(title = "Relationship Between Fox News Consumption and Voting Behavior",
+  labs(title = "Relationship between Fox News Consumption and Voting Behavior by Party",
        x = "Fox News",
@@
   scale_fill_brewer(palette = "Set1")
- # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
-  theme_minimal()
 ```
+@fig-foxnews and @fig-cnn take Fox News and CNN consumption into detail since they are the representation of Republican and Democratic network respectively.
+These two figures add in the respondents' party affiliation and examine if there is any differences in news consumption across different parties and their relationship with voting bahaviour.
+
+For @fig-foxnews, almost all Democrat identifying respondents voted for Biden and the majority of them do not watch Fox News.
+Conversely, most Republicans voted for Trump and a high proportions of them watch Fox News.
+However, notably there are more Republicans who did not watch Fox News choosing to vote for Biden instead compared to their Democrat counterparts.
+The relationship becomes interesting when the respondents identify either as "Independent" or "Other." It appears that independent voters who watch Fox News have a higher likelihood of voting for Trump while those who do not are more likely to vote for Biden.
+"Other" portrays the same relationship.
+
 ```{r}
+#| label: fig-cnn
+#| fig-cap: Relationship between CNN Consumption and Voting Behaviour by Party
+#| echo: false
+#| warning: false
+#| message: false
+
 # Change labels for Fox_News variable
-ces2020$CNN <- factor(ces2020$CNN, labels = c("No", "Yes"))
 
@@
   facet_wrap(facets = vars(Party)) +
-  labs(title = "Relationship Between CNN Consumption and Voting Behavior",
+  labs(title = "Relationship between CNN Consumption and Voting Behaviour by Party",
        x = "CNN",
@@
   scale_fill_brewer(palette = "Set1")
- # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
-  theme_minimal()
 ```
 
+@fig-cnn portrays nearly the same results as its Fox News counterpart.
+While most Democrat voters voted for Biden, the ones who do not watch CNN have a slightly higher chance of voting for Trump than the ones who do.
+Republicans who watch CNN also are more likely to vote for Biden compared to their counterparts that don't.
+The notable impact of network on Independent and Other voters is apparent as well.
+Independent voters who watch CNN are much more likely to vote for Biden while the ones that don't have a higher likelihood of voting for Trump.
+Others portray the same relationship.
+Because without the influence of media networks, the voting outcome for Indepdent and Other voters are almost evenly distributed between Biden and Trump, the results from the @fig-fox and @fig-cnn confirm the influence of media network on its viewers, and specifically its strong impact on viewers who neither are affiliated with the Democratic nor Republican party.
+The political opinions of viewers who do not have a strong party affiliation could be easily influenced by their news consumption.
+
 ```{r}
+#| label: fig-tv
+#| fig-cap: Relationship between TV News Consumption and Voting Behaviour by Party
+#| echo: false
+#| warning: false
+#| message: false
+
 ces2020$TV_type <- factor(ces2020$TV_type, labels = c("National & Local", "National"))
@@
   facet_wrap(facets = vars(Party)) +
-  labs(title = "Relationship Between TV News Consumption and Voting Behavior",
+  labs(title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
        x = "TV Type",
@@
 
-Our results are summarized in @tbl-modelresults.
+The relationship between voters' TV news consumption and their political and voting preferences are depicted in @fig-tv.
+Unlike the apparent influence of specific networks, different TV consumption seem to have no significant influence on voters voting behaviour.
+Democrat voters generally voted for Biden regardless if they choose to only watch national newscast or watch both national and local newscast, the same for Republicans.
+For Independent and other voters, there is generally a even number of people who voted for Biden or Trump across the two groups of people that watch different newscast.
 
+## Model Results
 ```{r}
@@
 
+The results, summarized in @tbl-modelresults1, generally matches our expectation.
+To avoid multicollinearity, the model excluded the category "Both" from `TV_type` and "Party Democrat" from `Party.`The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
+In this case, the estimated log-odds of supporting Biden for individuals who do not watch any of these news networks, watches both national and local newscasts, and identify as a Democrat is 3.63.
+
+@fig-modelresults1 (see @sec-credibility-interval) shows range of coefficient estimates of our model within the 90% probability.
+The estimates are statistically significant if the intervals do not cross 0.
+The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
+
+Neutral networks (ABC, CBS, and NBC) only have a slight positive relationship with voting for Biden, and their results are all statistically insignificant as shown in @fig-modelresults1.
+Watching CNN is significantly positively correlated with voting for Biden; compared to the reference group, voter watching CNN on average increases the log-odds of them voting for Biden by 1.631 units.
+MSNBC also exhibits similar relationship, while PBS shows a slightly smaller but still positive relationship.
+
+While only watching national newscast does decreases the likelihood of voting for Biden on a small scale compared to the reference group, there is no statistically significant relationship between the two.
+Lastly, as expected, identifying as part of the Republican party substantially decreases the possibility of voting for Biden (estimated coefficient of -5.484).
+Identifying as Independent or Other voters have no statistically significant influence on voting behaviours.
+
 ```{r}
@@
 summary(political_preferences)
-
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
 
@@
 #### Read data ####
-analysis_data1 <- read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
+# analysis_data1 <- read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
 
@@
 # Create voted_for variable in binary form
-analysis_data1$voted_for_binary <- ifelse(analysis_data1$voted_for == "Biden", 1, 0)
-
-# Model 1 for n = 1000
-set.seed(853)
-
-ces2020_reduced <- 
-  analysis_data1 |> 
-  slice_sample(n = 2500)
-
-posterior_vs_prior(political_preferences, size = 0.3) +
-  theme_minimal() +
-  theme(legend.position = "bottom") +
-  theme(axis.text.x=element_text(hjust=1, vjust=0.5),
-        text=element_text(size=8)) +
-  coord_flip()
+# analysis_data1$voted_for_binary <- ifelse(analysis_data1$voted_for == "Biden", 1, 0)
+# 
+# # Model 1 for n = 1000
+# set.seed(853)
+# 
+# ces2020_reduced <- 
+#   analysis_data1 |> 
+#   slice_sample(n = 2500)
+# 
+# posterior_vs_prior(political_preferences, size = 0.3) +
+#   theme_minimal() +
+#   theme(legend.position = "bottom") +
+#   theme(axis.text.x=element_text(hjust=1, vjust=0.5),
+#         text=element_text(size=8)) +
+#   coord_flip()
 ```

### 2024-04-12 paper/paper.tex
model, data, results! (whole day of hard work)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{siunitx}

  \newcolumntype{d}{S[
    input-open-uncertainty=,
    input-close-uncertainty=,
    parse-numbers = false,
    table-align-text-pre=false,
    table-align-text-post=false
  ]}

\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Hannah Yu},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at: LINK.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{Hannah Yu}
\date{April 11, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ces2020 }\OtherTok{\textless{}{-}}  \FunctionTok{read\_parquet}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data/analysis\_data/cleaned\_ces2020.parquet"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

You can and should cross-reference sections and sub-sections. We use R
Core Team (2023) and Wickham et al. (2019).

The remainder of this paper is structured as follows.
Section~\ref{sec-data}\ldots.

\hypertarget{sec-data}{%
\section{Data}\label{sec-data}}

Data analysis is performed using statistical programming language R (R
Core Team 2023), with packages \texttt{tidyverse}
(\textbf{citeTidyverse?}), \texttt{here} (\textbf{citeHere?}),
\texttt{rstanarm} (\textbf{citeRstanarm?}), \texttt{modelsummary}
(\textbf{citeModleSummary?}), \texttt{ggplot2} (\textbf{citeGgplot2?}),
\texttt{knitr} (\textbf{citeKnitr?}), \texttt{marginaleffects}
(\textbf{citeMarginalEffects?}), \texttt{plotly} (\textbf{citePlotly?}),
\texttt{tibble} (\textbf{citeTibble?}), \texttt{margins}
(\textbf{citeMargins?}), \texttt{testthat} (\textbf{citetestthat?}) and
\texttt{kableExtra} (\textbf{citeKableExtra?}).

\hypertarget{data-source}{%
\subsection{Data Source}\label{data-source}}

Data for this research comes from the 2020 Cooperative Election Study
(CES) (\textbf{citeCes2020?}), a annual US political survey. The CES
contains information about Americans' political view, voting behaviours
and experiences across various political geography and social context.
61,000 American adults participated in the survey in 2020.

\hypertarget{data-cleaning-and-variables}{%
\subsection{Data Cleaning and
Variables}\label{data-cleaning-and-variables}}

\hypertarget{tbl-clean-data}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1408}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0563}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0563}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0563}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0563}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1268}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0845}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0563}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.0845}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1127}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 20\tabcolsep) * \real{0.1690}}@{}}
\caption{\label{tbl-clean-data}Preview of the cleaned 2020 CES
dataset}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
voted\_for
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
ABC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
NBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CNN
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fox\_News
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MSNBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
PBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
TV\_type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Party
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
voted\_for
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
ABC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
NBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CNN
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fox\_News
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MSNBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
PBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
TV\_type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Party
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Trump & Yes & Yes & Yes & Yes & Yes & No & No & No & Both &
Republican \\
Biden & Yes & Yes & Yes & No & No & Yes & No & No & Both &
Independent \\
Biden & Yes & No & No & No & No & No & No & No & Both & Independent \\
Trump & No & No & No & No & Yes & Yes & No & No & Both & Republican \\
Biden & No & No & Yes & Yes & No & Yes & No & No & Both & Democrat \\
\end{longtable}

\hypertarget{tbl-summary}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0221}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0882}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.0735}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.1765}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 22\tabcolsep) * \real{0.1250}}@{}}
\caption{\label{tbl-summary}Statistics summary of the cleaned 2020 CES
dataset}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
voted\_for
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
ABC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
NBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CNN
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fox\_News
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MSNBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
PBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
TV\_type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Party
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
voted\_for
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
ABC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
NBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CNN
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fox\_News
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MSNBC
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
PBS
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Other
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
TV\_type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Party
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
& Trump: 7884 & Yes: 7402 & Yes: 6650 & Yes: 7333 & Yes: 8311 & Yes:
8384 & No :14444 & No :18073 & No :19222 & Local Newscast : 0 & Democrat
:9819 \\
& Biden:13328 & No :13810 & No :14562 & No :13879 & No :12901 & No
:12828 & Yes: 6768 & Yes: 3139 & Yes: 1990 & National Newscast: 7422 &
Republican :5642 \\
& NA & NA & NA & NA & NA & NA & NA & NA & NA & Both :13790 &
Independent:5217 \\
& NA & NA & NA & NA & NA & NA & NA & NA & NA & NA & Other : 534 \\
\end{longtable}

Table~\ref{tbl-summary} presentts a summary of the cleaned data, showing
detailed statistics about the dataset. Iis evident that Biden has more
supporters in this election. The seven listed media networks capture the
majority networks people watch; while \texttt{Other} captures the rest.
Due to the small number of respondents that only watch local newscast,

As we can see from the table, there are more people who support Biden.
Respondents covered a wide range of races, with white people being the
most heavily represented. Also, CES data came from a variety of
locations, but the majority came from the southern region of the United
States. The employment status of those who completed the survey varied,
with most of them being full-time or retired.

Since this paper focuses on analyzing the influence of media usage on
registered voters decision, I perform the following data cleaning
process and selected the related variables. The dataset is cleaned by
renaming the column names, changing the variable for from categorical to
dummy, selecting the variables of interest, and filtering out missing
information and information not related to the study. After cleaning,
there are 10331 rows of data remain in the cleaned dataset.
Table~\ref{tbl-clean-data} shows a preview of the cleaned dataset.

The dependent variable of my examination is: \texttt{presvote20post},
renamed to \texttt{voted\_for}. This variable represents the
presidential candidate the respondent voted for in the 2020 election in
the form of a numerical variable. The variable \texttt{votereg}
represents whether the respondent is registered to vote using numerical
numbers. This paper will only analyze respondents who are registered to
vote and focus on the outcome of two candidates, Joe Biden representing
the Democratic party and Donald Trump representing the Republican party.
To analyze the observations of interest, I first limited the
observations to the ones that responded ``Yes'' in \texttt{votereg}. And
I filtered the responses in \texttt{presvote20post} to only ``Biden'' or
``Trump'' and converted the variable into a dummy variable where 1
represents ``Biden'' and 0 represents ``Trump''. Rest of the variable
this paper focuses on are being divided into three categories: Media Use
- Networks, Media Use - TV Type, and Party Affiliation.

Media Use - Networks:

\begin{itemize}
\item
  \texttt{CC20\_300b\_1}, renamed to \texttt{ABC},

  \begin{itemize}
  \tightlist
  \item
    This variable reports if the respondent watches ABC. A value of 1
    signifies that the respondent does watch ABC, while 2 indicates
    otherwise. This variable was converted into a dummy variable, where
    1 represents ``Yes'' and 0 represents ``No''.
  \end{itemize}
\item
  \texttt{CC20\_300b\_2}, renamed to \texttt{CBS},

  \begin{itemize}
  \tightlist
  \item
    This variable reports if the respondent watches CBS. A value of 1
    signifies that the respondent does watch CBS, while 2 indicates
    otherwise. This variable was converted into a dummy variable, where
    1 represents ``Yes'' and 0 represents ``No''.
  \end{itemize}
\item
  \texttt{CC20\_300b\_3}, renamed to \texttt{NBC};
  \texttt{CC20\_300b\_4}, renamed to \texttt{CNN};
  \texttt{CC20\_300b\_5}, renamed to \texttt{Fox\_News};
  \texttt{CC20\_300b\_6}, renamed to \texttt{MSNBC};
  \texttt{CC20\_300b\_7}, renamed to \texttt{PBS};
  \texttt{CC20\_300b\_8}, renamed to \texttt{Other},

  \begin{itemize}
  \tightlist
  \item
    The interpretation and cleaning process of these variables are the
    same as \texttt{CBS} and \texttt{ABC}.
  \end{itemize}
\end{itemize}

Media Use - TV Type:

\begin{itemize}
\item
  \texttt{CC20\_300a}, renamed to \texttt{TV\_type},

  \begin{itemize}
  \tightlist
  \item
    This variable reports on what kind of TV news the respondent
    watches. A value of 1 signifies that the respondent watches ``Local
    Newcast'', 2 signifies ``National Newscast''; 3 ``Both''.
  \end{itemize}
\end{itemize}

Party Affiliation:

\begin{itemize}
\item
  \texttt{CC20\_433a}, renamed to \texttt{Party},

  \begin{itemize}
  \tightlist
  \item
    This variable reports if the respondent political party affiliation.
    A value of 1 signifies that the respondent identifies as
    ``Democrat'', 2 signifies ``Republican''; 3 ``Indepdent'', and 4
    ``Other''.
  \end{itemize}
\end{itemize}

Table~\ref{tbl-summary} presentts a summary of the cleaned data, showing
detailed statistics about the dataset. Iis evident that Biden has more
supporters in this election.

As we can see from the table, there are more people who support Biden.
Respondents covered a wide range of races, with white people being the
most heavily represented. Also, CES data came from a variety of
locations, but the majority came from the southern region of the United
States. The employment status of those who completed the survey varied,
with most of them being full-time or retired.

\hypertarget{data-measurement}{%
\subsection{Data Measurement}\label{data-measurement}}

Because the data was collected from surveys, there might be some
inconsistencies and misinterpretations of the questions in people's
responses. Therefore this section disects on what the variables are
measuring.

each of our variable is only representable for the following scenarios.

Firstly, for the variable ``votereg'' indicating whether a respondent is
registered to vote, the variable relies on self-reported information
from survey respondents. Due to the inefficiencies of the US voter
registration system, people who misunderstood their voter registration
status might falsely reported their condition. For example, some
individuals might believe they reached the status simply because they
are of age but did not actually register at their local office.
According to (\textbf{inaccurate?}), there are millions of voter
registrations that are no longer valid or inaccurate.

Representing the presidential candidate the respondent voted for,
``CC20\_410'' takes into account of recall bias and social desirability
bias along with people's reported presidential candidate preference.
Trump had made many controversial speeches throughout his presidency
that contributed to his polarizing image and unpopularity in mainstream
media. Therefore, many of his voters would conceal their support due to
social pressure, potentially leading to under-reporting of votes for
Trump in the survey data.

People's media use networks is being represented by if ``ABC'', ``CBS'',
``NBC'', ``CNN'', ``Fox\_News'', ``MSNBC'', ``PBS'', and ``Other''. also
rely on people's self-reported preferences.

For the variable ``race,'' which denotes the racial or ethnic group of
the respondent, categorization relies on self-identification. However,
racial identity is complex and can be influenced by cultural, social,
and historical factors. Mixed-race individuals, for instance, may choose
to identify with one racial group over another based on social
preferences or personal experiences. Moreover, the race variable
includes a category for ``two or more races'' to classify individuals
identifying with multiple racial backgrounds. While this acknowledges
the diversity within the population, it may not capture the nuances of
each individual's identity. Additionally, the absence of a distinct
category for ``Indians or South Asians'' presents a limitation. While
these individuals may technically fall under the category ``Asian,''
many Indian and South Asian Americans may prefer to identify separately
due to differences in appearance and cultural background. The term
``Asians'' are more generally associated with East Asians such as
Chinese, Japanese, and Koreans. As a result, there's a potential for
misclassification, with some individuals opting to report themselves as
belonging to the ``other'' race category instead.

In the case of ``region,'' which represents the census region where the
respondent lives, data collection relies on categorization based on
geographical location. However, it's important to note that regional
boundaries can sometimes be arbitrary and may not fully capture the
diverse cultural, economic, and social affiliations of individuals.
Additionally, people living in bordering states or areas near regional
boundaries may have affiliations with multiple regions or may identify
more strongly with a neighboring region. For example, states like
Missouri and Kentucky are often considered part of the Midwest, but they
also share cultural and economic ties with the South. This complexity
can lead to challenges in accurately categorizing individuals based on
their region of residence, potentially resulting in oversimplification
or misrepresentation of regional identities and characteristics.

The ``region'' variable categorizes respondents based on their
geographical location into four census regions: Northeast, Midwest,
South, and West. However, regional boundaries can be arbitrary, and
individuals living in bordering areas may have affiliations with
multiple regions or identify more strongly with a neighboring region.
For instance, states like Missouri and Kentucky are often considered
part of the Midwest but also share cultural and economic ties with the
South. This complexity can make individuals accurately reporting their
region challenging.

Finally, for ``employ'', indicating the respondent's self-reporting
employment status, can be influenced by various factors such as job
changes, seasonal work, and personal circumstances. In addition,
individuals may intentionally misreport their employment status due to
societal pressures or to access benefits. For instance, some may falsely
claim employment to avoid stigma, while others may report unemployment
to qualify for unemployment benefits. Additionally, students working
part-time jobs may selectively report their status based on their
perceived benefit. These inconsistencies can introduce bias and
inaccuracies into the data, impacting the reliability of our analyses.

\hypertarget{model}{%
\section{Model}\label{model}}

The goal of our modelling strategy is twofold. Firstly,\ldots{}

Here we briefly describe the Bayesian analysis model used to
investigate\ldots{} Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\hypertarget{model-set-up}{%
\subsection{Model set-up}\label{model-set-up}}

I utilized a Bayesian logistic regression model to examine the
relationship between voters' political preferences and their media use
preferences.The model is formulated as follows:

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox_News}_i + \beta_6 \times \mbox{MSNBC}_i + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV_type}_i + \beta_{10} \times \mbox{Party}_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
\beta_5 &\sim \mbox{Normal}(0, 2.5) \\
\beta_6 &\sim \mbox{Normal}(0, 2.5) \\
\beta_7 &\sim \mbox{Normal}(0, 2.5) \\
\beta_8 &\sim \mbox{Normal}(0, 2.5) \\
\beta_9 &\sim \mbox{Normal}(0, 2.5) \\
\beta_10 &\sim \mbox{Normal}(0, 2.5)
\end{align}

In this model, \(y_i\) represents the binary outcome variable indicating
whether an individual voted Biden (as opposed to Trump). The probability
of voting for the Biden (\(\pi_i\)) is modeled using a logistic link
function (\text{logit}(\(\pi_i\))), which is a linear combination of the
intercept (\(\alpha\)) and the coefficients (\(\beta_1\), \(\beta_2\),
\(\beta_3\), \(\beta_4\), \(\beta_5\), \(\beta_6\), \(\beta_7\),
\(\beta_8\), \(\beta_9\), \(\beta_10\))) corresponding to the predictor
variables media use networks, TV news type, and party affiliations,
respectively. Media use networks are being represented by the following
predictor variables: \text{ABC}\_i, \text{CBS}\_i, \text{NBC}\_i,
\text{CNN}\_i, \text{Fox_News}\_i \text{MSNBC}\_i ,\text{PBS}\_i, and
\text{Other}\_i. The rest of the predictor variables are denoted as
\text{TV_type}\_i and \text{Party}\_i, where \(i\) indexes the
individuals in the dataset.

The intercept and coefficients are assigned informative prior
distributions to regularize the model. Specifically, a normal
distribution with a mean of 0 and a standard deviation of 2.5 for each
parameter is assumed.

This modeling approach is chosen for several reasons. Firstly, logistic
regression is well-suited for binary outcome variables, making it
appropriate for analyzing voting behavior. Additionally, Bayesian
methods enables the incorporation of prior knowledge and uncertainty
into our analysis, which provides more robust estimates of the model
parameters. Alternative modeling approaches, such as linear regression
models, were also considered. However, Bayesian logistic regression is
chosen to fit the resulting binary variable of voter's decision.

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of (\textbf{citeRstanarm?}). We use the default priors from
\texttt{rstanarm}. Rstanarm employs Markov chain Monte Carlo (MCMC)
techniques to estimate the posterior distribution of the parameters. To
avoid excessive runtime, we randomly sampled 2500 observations to fit
the model. Model diagnostics, including convergence checks and posterior
summaries, are available in the supplementary materials (see Appendix
Section~\ref{sec-model-details}).

\hypertarget{model-justification}{%
\subsubsection{Model justification}\label{model-justification}}

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# \# Create individual plots for each news channel}
\CommentTok{\# plot\_ABC \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(ABC))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "ABC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_CBS \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(CBS))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "CBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_NBC \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(NBC))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "NBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_CNN \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(CNN))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "CNN", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_Fox\_News \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(Fox\_News))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "Fox News", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\# \#  facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_MSNBC \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(MSNBC))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "MSNBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\# \#  facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_PBS \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(PBS))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() }
\CommentTok{\# }
\CommentTok{\# plot\_Other \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(Other))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# }
\CommentTok{\# legend \textless{}{-} g\_legend(plot\_PBS + theme(legend.position=\textquotesingle{}bottom\textquotesingle{}))}
\CommentTok{\# }
\CommentTok{\# grid.arrange(plot\_ABC, plot\_CBS, plot\_NBC, plot\_CNN, plot\_Fox\_News, plot\_MSNBC, plot\_PBS + theme(legend.position =\textquotesingle{}none\textquotesingle{}), plot\_Other, legend, nrow = 3)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create individual plots for each news channel}
\CommentTok{\# plot\_post \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(post))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "Posted", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   theme(plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 4000)) +  }
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_comment \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(comment))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "Commented", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 4000)) +  }
\CommentTok{\#   theme(axis.title.y = element\_blank(), axis.text.y = element\_blank(), axis.ticks.y = element\_blank(), plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_read \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(read))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "Read", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 4000)) +}
\CommentTok{\#   theme(axis.title.y = element\_blank(), axis.text.y = element\_blank(), axis.ticks.y = element\_blank(), plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_follow \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(follow))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "Followed", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 4000)) +}
\CommentTok{\#   theme(plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_forward \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(forward))) +}
\CommentTok{\#   geom\_bar(position = "dodge") +}
\CommentTok{\#   labs(title = "Forwarded", x = "Vote", y = "Count") +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 4000)) +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   theme(axis.title.y = element\_blank(), axis.text.y = element\_blank(), axis.ticks.y = element\_blank(), plot.title = element\_text(hjust = 0.5)) }
\CommentTok{\# }
\CommentTok{\# }
\CommentTok{\# legend \textless{}{-} g\_legend(plot\_forward + theme(legend.position=\textquotesingle{}bottom\textquotesingle{}, }
\CommentTok{\#                                         legend.text = element\_text(size = 15, face="bold"), }
\CommentTok{\#                                         legend.title = element\_blank()))}
\CommentTok{\# }
\CommentTok{\# grid.arrange(plot\_post, plot\_comment, plot\_read, plot\_follow, plot\_forward + theme(legend.position =\textquotesingle{}none\textquotesingle{}), legend, nrow = 2)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create individual plots for each news channel}
\CommentTok{\# plot\_post \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(post, levels = c("not\_selected", "selected")))) +}
\CommentTok{\#   geom\_bar(position = "stack", stat = "count") +}
\CommentTok{\#   labs(title = "Posted", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   theme(plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 6000)) +  }
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_comment \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(comment, levels = c("not\_selected", "selected")))) +}
\CommentTok{\#   geom\_bar(position = "stack", stat = "count") +}
\CommentTok{\#   labs(title = "Commented", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 6000)) +  }
\CommentTok{\#   theme(axis.title.y = element\_blank(), axis.text.y = element\_blank(), axis.ticks.y = element\_blank(), plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_read \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(read, levels = c("not\_selected", "selected")))) +}
\CommentTok{\#   geom\_bar(position = "stack", stat = "count") +}
\CommentTok{\#   labs(title = "Read", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 6000)) +}
\CommentTok{\#   theme(axis.title.y = element\_blank(), axis.text.y = element\_blank(), axis.ticks.y = element\_blank(), plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_follow \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(follow, levels = c("not\_selected", "selected")))) +}
\CommentTok{\#   geom\_bar(position = "stack", stat = "count") +}
\CommentTok{\#   labs(title = "Followed", x = "Vote", y = "Count") +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 6000)) +}
\CommentTok{\#   theme(plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#   theme(axis.title.y = element\_blank(), axis.text.y = element\_blank(), axis.ticks.y = element\_blank(), plot.title = element\_text(hjust = 0.5)) +}
\CommentTok{\#   guides(fill = FALSE)}
\CommentTok{\# }
\CommentTok{\# plot\_forward \textless{}{-} ggplot(ces2020, aes(x = factor(voted\_for), fill = factor(forward, levels = c("not\_selected", "selected")))) +}
\CommentTok{\#   geom\_bar(position = "stack", stat = "count") +}
\CommentTok{\#   labs(title = "Forwarded", x = "Vote", y = "Count") +}
\CommentTok{\#   coord\_cartesian(ylim = c(0, 6000)) +}
\CommentTok{\#   theme\_minimal() +}
\CommentTok{\#   theme(axis.title.y = element\_blank(), axis.text.y = element\_blank(), axis.ticks.y = element\_blank(), plot.title = element\_text(hjust = 0.5)) }
\CommentTok{\#  \# facet\_wrap(\textasciitilde{} ., ncol = 4) +}
\CommentTok{\# }
\CommentTok{\# }
\CommentTok{\# \#legend \textless{}{-} g\_legend(plot\_forward + theme(legend.position=\textquotesingle{}bottom\textquotesingle{}, }
\CommentTok{\#                                         \#legend.text = element\_text(size = 15, face="bold"), }
\CommentTok{\#                                        \# legend.title = element\_blank())}
\CommentTok{\# }
\CommentTok{\# grid.arrange(plot\_post, plot\_comment, plot\_read, plot\_follow, plot\_forward + theme(legend.position =\textquotesingle{}none\textquotesingle{}), nrow = 1)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Change labels for Fox\_News variable}
\NormalTok{ces2020}\SpecialCharTok{$}\NormalTok{Fox\_News }\OtherTok{\textless{}{-}} \FunctionTok{factor}\NormalTok{(ces2020}\SpecialCharTok{$}\NormalTok{Fox\_News, }\AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"No"}\NormalTok{, }\StringTok{"Yes"}\NormalTok{))}

\FunctionTok{ggplot}\NormalTok{(ces2020, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Fox\_News, }\AttributeTok{fill =}\NormalTok{ voted\_for)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\AttributeTok{facets =} \FunctionTok{vars}\NormalTok{(Party)) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Relationship Between Fox News Consumption and Voting Behavior"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Fox News"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{color =} \StringTok{"Voted for Biden (1) or Trump (0)"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_brewer}\NormalTok{(}\AttributeTok{palette =} \StringTok{"Set1"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/unnamed-chunk-9-1.pdf}

}

\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
 \CommentTok{\# scale\_color\_manual(values = c("red", "blue")) +  \# Customize colors for better visibility}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
List of 136
 $ line                            :List of 6
  ..$ colour       : chr "black"
  ..$ linewidth    : num 0.5
  ..$ linetype     : num 1
  ..$ lineend      : chr "butt"
  ..$ arrow        : logi FALSE
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_line" "element"
 $ rect                            :List of 5
  ..$ fill         : chr "white"
  ..$ colour       : chr "black"
  ..$ linewidth    : num 0.5
  ..$ linetype     : num 1
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_rect" "element"
 $ text                            :List of 11
  ..$ family       : chr ""
  ..$ face         : chr "plain"
  ..$ colour       : chr "black"
  ..$ size         : num 11
  ..$ hjust        : num 0.5
  ..$ vjust        : num 0.5
  ..$ angle        : num 0
  ..$ lineheight   : num 0.9
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : logi FALSE
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ title                           : NULL
 $ aspect.ratio                    : NULL
 $ axis.title                      : NULL
 $ axis.title.x                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 2.75points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.x.top                :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 0
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 2.75points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.x.bottom             : NULL
 $ axis.title.y                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : num 90
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.75points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.y.left               : NULL
 $ axis.title.y.right              :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : num -90
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 2.75points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text                       :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : chr "grey30"
  ..$ size         : 'rel' num 0.8
  ..$ hjust        : NULL
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 2.2points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x.top                 :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 0
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 2.2points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x.bottom              : NULL
 $ axis.text.y                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 1
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.2points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.y.left                : NULL
 $ axis.text.y.right               :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 2.2points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.theta                 : NULL
 $ axis.text.r                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0.5
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.2points 0points 2.2points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.ticks                      : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ axis.ticks.x                    : NULL
 $ axis.ticks.x.top                : NULL
 $ axis.ticks.x.bottom             : NULL
 $ axis.ticks.y                    : NULL
 $ axis.ticks.y.left               : NULL
 $ axis.ticks.y.right              : NULL
 $ axis.ticks.theta                : NULL
 $ axis.ticks.r                    : NULL
 $ axis.minor.ticks.x.top          : NULL
 $ axis.minor.ticks.x.bottom       : NULL
 $ axis.minor.ticks.y.left         : NULL
 $ axis.minor.ticks.y.right        : NULL
 $ axis.minor.ticks.theta          : NULL
 $ axis.minor.ticks.r              : NULL
 $ axis.ticks.length               : 'simpleUnit' num 2.75points
  ..- attr(*, "unit")= int 8
 $ axis.ticks.length.x             : NULL
 $ axis.ticks.length.x.top         : NULL
 $ axis.ticks.length.x.bottom      : NULL
 $ axis.ticks.length.y             : NULL
 $ axis.ticks.length.y.left        : NULL
 $ axis.ticks.length.y.right       : NULL
 $ axis.ticks.length.theta         : NULL
 $ axis.ticks.length.r             : NULL
 $ axis.minor.ticks.length         : 'rel' num 0.75
 $ axis.minor.ticks.length.x       : NULL
 $ axis.minor.ticks.length.x.top   : NULL
 $ axis.minor.ticks.length.x.bottom: NULL
 $ axis.minor.ticks.length.y       : NULL
 $ axis.minor.ticks.length.y.left  : NULL
 $ axis.minor.ticks.length.y.right : NULL
 $ axis.minor.ticks.length.theta   : NULL
 $ axis.minor.ticks.length.r       : NULL
 $ axis.line                       : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ axis.line.x                     : NULL
 $ axis.line.x.top                 : NULL
 $ axis.line.x.bottom              : NULL
 $ axis.line.y                     : NULL
 $ axis.line.y.left                : NULL
 $ axis.line.y.right               : NULL
 $ axis.line.theta                 : NULL
 $ axis.line.r                     : NULL
 $ legend.background               : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.margin                   : 'margin' num [1:4] 5.5points 5.5points 5.5points 5.5points
  ..- attr(*, "unit")= int 8
 $ legend.spacing                  : 'simpleUnit' num 11points
  ..- attr(*, "unit")= int 8
 $ legend.spacing.x                : NULL
 $ legend.spacing.y                : NULL
 $ legend.key                      : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.key.size                 : 'simpleUnit' num 1.2lines
  ..- attr(*, "unit")= int 3
 $ legend.key.height               : NULL
 $ legend.key.width                : NULL
 $ legend.key.spacing              : 'simpleUnit' num 5.5points
  ..- attr(*, "unit")= int 8
 $ legend.key.spacing.x            : NULL
 $ legend.key.spacing.y            : NULL
 $ legend.frame                    : NULL
 $ legend.ticks                    : NULL
 $ legend.ticks.length             : 'rel' num 0.2
 $ legend.axis.line                : NULL
 $ legend.text                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : 'rel' num 0.8
  ..$ hjust        : NULL
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ legend.text.position            : NULL
 $ legend.title                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ legend.title.position           : NULL
 $ legend.position                 : chr "right"
 $ legend.position.inside          : NULL
 $ legend.direction                : NULL
 $ legend.byrow                    : NULL
 $ legend.justification            : chr "center"
 $ legend.justification.top        : NULL
 $ legend.justification.bottom     : NULL
 $ legend.justification.left       : NULL
 $ legend.justification.right      : NULL
 $ legend.justification.inside     : NULL
 $ legend.location                 : NULL
 $ legend.box                      : NULL
 $ legend.box.just                 : NULL
 $ legend.box.margin               : 'margin' num [1:4] 0cm 0cm 0cm 0cm
  ..- attr(*, "unit")= int 1
 $ legend.box.background           : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.box.spacing              : 'simpleUnit' num 11points
  ..- attr(*, "unit")= int 8
  [list output truncated]
 - attr(*, "class")= chr [1:2] "theme" "gg"
 - attr(*, "complete")= logi TRUE
 - attr(*, "validate")= logi TRUE
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Change labels for Fox\_News variable}
\NormalTok{ces2020}\SpecialCharTok{$}\NormalTok{CNN }\OtherTok{\textless{}{-}} \FunctionTok{factor}\NormalTok{(ces2020}\SpecialCharTok{$}\NormalTok{CNN, }\AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"No"}\NormalTok{, }\StringTok{"Yes"}\NormalTok{))}

\FunctionTok{ggplot}\NormalTok{(ces2020, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ CNN, }\AttributeTok{fill =}\NormalTok{ voted\_for)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\AttributeTok{facets =} \FunctionTok{vars}\NormalTok{(Party)) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Relationship Between CNN Consumption and Voting Behavior"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"CNN"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{color =} \StringTok{"Voted for Biden (1) or Trump (0)"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_brewer}\NormalTok{(}\AttributeTok{palette =} \StringTok{"Set1"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/unnamed-chunk-10-1.pdf}

}

\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
 \CommentTok{\# scale\_color\_manual(values = c("red", "blue")) +  \# Customize colors for better visibility}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
List of 136
 $ line                            :List of 6
  ..$ colour       : chr "black"
  ..$ linewidth    : num 0.5
  ..$ linetype     : num 1
  ..$ lineend      : chr "butt"
  ..$ arrow        : logi FALSE
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_line" "element"
 $ rect                            :List of 5
  ..$ fill         : chr "white"
  ..$ colour       : chr "black"
  ..$ linewidth    : num 0.5
  ..$ linetype     : num 1
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_rect" "element"
 $ text                            :List of 11
  ..$ family       : chr ""
  ..$ face         : chr "plain"
  ..$ colour       : chr "black"
  ..$ size         : num 11
  ..$ hjust        : num 0.5
  ..$ vjust        : num 0.5
  ..$ angle        : num 0
  ..$ lineheight   : num 0.9
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : logi FALSE
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ title                           : NULL
 $ aspect.ratio                    : NULL
 $ axis.title                      : NULL
 $ axis.title.x                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 2.75points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.x.top                :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 0
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 2.75points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.x.bottom             : NULL
 $ axis.title.y                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : num 90
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.75points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.y.left               : NULL
 $ axis.title.y.right              :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : num -90
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 2.75points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text                       :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : chr "grey30"
  ..$ size         : 'rel' num 0.8
  ..$ hjust        : NULL
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 2.2points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x.top                 :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 0
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 2.2points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x.bottom              : NULL
 $ axis.text.y                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 1
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.2points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.y.left                : NULL
 $ axis.text.y.right               :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 2.2points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.theta                 : NULL
 $ axis.text.r                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0.5
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.2points 0points 2.2points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.ticks                      : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ axis.ticks.x                    : NULL
 $ axis.ticks.x.top                : NULL
 $ axis.ticks.x.bottom             : NULL
 $ axis.ticks.y                    : NULL
 $ axis.ticks.y.left               : NULL
 $ axis.ticks.y.right              : NULL
 $ axis.ticks.theta                : NULL
 $ axis.ticks.r                    : NULL
 $ axis.minor.ticks.x.top          : NULL
 $ axis.minor.ticks.x.bottom       : NULL
 $ axis.minor.ticks.y.left         : NULL
 $ axis.minor.ticks.y.right        : NULL
 $ axis.minor.ticks.theta          : NULL
 $ axis.minor.ticks.r              : NULL
 $ axis.ticks.length               : 'simpleUnit' num 2.75points
  ..- attr(*, "unit")= int 8
 $ axis.ticks.length.x             : NULL
 $ axis.ticks.length.x.top         : NULL
 $ axis.ticks.length.x.bottom      : NULL
 $ axis.ticks.length.y             : NULL
 $ axis.ticks.length.y.left        : NULL
 $ axis.ticks.length.y.right       : NULL
 $ axis.ticks.length.theta         : NULL
 $ axis.ticks.length.r             : NULL
 $ axis.minor.ticks.length         : 'rel' num 0.75
 $ axis.minor.ticks.length.x       : NULL
 $ axis.minor.ticks.length.x.top   : NULL
 $ axis.minor.ticks.length.x.bottom: NULL
 $ axis.minor.ticks.length.y       : NULL
 $ axis.minor.ticks.length.y.left  : NULL
 $ axis.minor.ticks.length.y.right : NULL
 $ axis.minor.ticks.length.theta   : NULL
 $ axis.minor.ticks.length.r       : NULL
 $ axis.line                       : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ axis.line.x                     : NULL
 $ axis.line.x.top                 : NULL
 $ axis.line.x.bottom              : NULL
 $ axis.line.y                     : NULL
 $ axis.line.y.left                : NULL
 $ axis.line.y.right               : NULL
 $ axis.line.theta                 : NULL
 $ axis.line.r                     : NULL
 $ legend.background               : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.margin                   : 'margin' num [1:4] 5.5points 5.5points 5.5points 5.5points
  ..- attr(*, "unit")= int 8
 $ legend.spacing                  : 'simpleUnit' num 11points
  ..- attr(*, "unit")= int 8
 $ legend.spacing.x                : NULL
 $ legend.spacing.y                : NULL
 $ legend.key                      : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.key.size                 : 'simpleUnit' num 1.2lines
  ..- attr(*, "unit")= int 3
 $ legend.key.height               : NULL
 $ legend.key.width                : NULL
 $ legend.key.spacing              : 'simpleUnit' num 5.5points
  ..- attr(*, "unit")= int 8
 $ legend.key.spacing.x            : NULL
 $ legend.key.spacing.y            : NULL
 $ legend.frame                    : NULL
 $ legend.ticks                    : NULL
 $ legend.ticks.length             : 'rel' num 0.2
 $ legend.axis.line                : NULL
 $ legend.text                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : 'rel' num 0.8
  ..$ hjust        : NULL
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ legend.text.position            : NULL
 $ legend.title                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ legend.title.position           : NULL
 $ legend.position                 : chr "right"
 $ legend.position.inside          : NULL
 $ legend.direction                : NULL
 $ legend.byrow                    : NULL
 $ legend.justification            : chr "center"
 $ legend.justification.top        : NULL
 $ legend.justification.bottom     : NULL
 $ legend.justification.left       : NULL
 $ legend.justification.right      : NULL
 $ legend.justification.inside     : NULL
 $ legend.location                 : NULL
 $ legend.box                      : NULL
 $ legend.box.just                 : NULL
 $ legend.box.margin               : 'margin' num [1:4] 0cm 0cm 0cm 0cm
  ..- attr(*, "unit")= int 1
 $ legend.box.background           : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.box.spacing              : 'simpleUnit' num 11points
  ..- attr(*, "unit")= int 8
  [list output truncated]
 - attr(*, "class")= chr [1:2] "theme" "gg"
 - attr(*, "complete")= logi TRUE
 - attr(*, "validate")= logi TRUE
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ces2020}\SpecialCharTok{$}\NormalTok{TV\_type }\OtherTok{\textless{}{-}} \FunctionTok{factor}\NormalTok{(ces2020}\SpecialCharTok{$}\NormalTok{TV\_type, }\AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"National \& Local"}\NormalTok{, }\StringTok{"National"}\NormalTok{))}

\NormalTok{scatter\_plot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(ces2020, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ TV\_type, }\AttributeTok{fill =}\NormalTok{ voted\_for)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\AttributeTok{facets =} \FunctionTok{vars}\NormalTok{(Party)) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Relationship Between TV News Consumption and Voting Behavior"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"TV Type"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{color =} \StringTok{"Voted for Biden (1) or Trump (0)"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_brewer}\NormalTok{(}\AttributeTok{palette =} \StringTok{"Set1"}\NormalTok{)}
 \CommentTok{\# scale\_color\_manual(values = c("red", "blue")) +  \# Customize colors for better visibility}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
List of 136
 $ line                            :List of 6
  ..$ colour       : chr "black"
  ..$ linewidth    : num 0.5
  ..$ linetype     : num 1
  ..$ lineend      : chr "butt"
  ..$ arrow        : logi FALSE
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_line" "element"
 $ rect                            :List of 5
  ..$ fill         : chr "white"
  ..$ colour       : chr "black"
  ..$ linewidth    : num 0.5
  ..$ linetype     : num 1
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_rect" "element"
 $ text                            :List of 11
  ..$ family       : chr ""
  ..$ face         : chr "plain"
  ..$ colour       : chr "black"
  ..$ size         : num 11
  ..$ hjust        : num 0.5
  ..$ vjust        : num 0.5
  ..$ angle        : num 0
  ..$ lineheight   : num 0.9
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : logi FALSE
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ title                           : NULL
 $ aspect.ratio                    : NULL
 $ axis.title                      : NULL
 $ axis.title.x                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 2.75points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.x.top                :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 0
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 2.75points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.x.bottom             : NULL
 $ axis.title.y                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : num 90
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.75points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.title.y.left               : NULL
 $ axis.title.y.right              :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : num -90
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 2.75points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text                       :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : chr "grey30"
  ..$ size         : 'rel' num 0.8
  ..$ hjust        : NULL
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 1
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 2.2points 0points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x.top                 :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : NULL
  ..$ vjust        : num 0
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 2.2points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.x.bottom              : NULL
 $ axis.text.y                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 1
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.2points 0points 0points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.y.left                : NULL
 $ axis.text.y.right               :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 0points 0points 2.2points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.text.theta                 : NULL
 $ axis.text.r                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0.5
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : 'margin' num [1:4] 0points 2.2points 0points 2.2points
  .. ..- attr(*, "unit")= int 8
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ axis.ticks                      : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ axis.ticks.x                    : NULL
 $ axis.ticks.x.top                : NULL
 $ axis.ticks.x.bottom             : NULL
 $ axis.ticks.y                    : NULL
 $ axis.ticks.y.left               : NULL
 $ axis.ticks.y.right              : NULL
 $ axis.ticks.theta                : NULL
 $ axis.ticks.r                    : NULL
 $ axis.minor.ticks.x.top          : NULL
 $ axis.minor.ticks.x.bottom       : NULL
 $ axis.minor.ticks.y.left         : NULL
 $ axis.minor.ticks.y.right        : NULL
 $ axis.minor.ticks.theta          : NULL
 $ axis.minor.ticks.r              : NULL
 $ axis.ticks.length               : 'simpleUnit' num 2.75points
  ..- attr(*, "unit")= int 8
 $ axis.ticks.length.x             : NULL
 $ axis.ticks.length.x.top         : NULL
 $ axis.ticks.length.x.bottom      : NULL
 $ axis.ticks.length.y             : NULL
 $ axis.ticks.length.y.left        : NULL
 $ axis.ticks.length.y.right       : NULL
 $ axis.ticks.length.theta         : NULL
 $ axis.ticks.length.r             : NULL
 $ axis.minor.ticks.length         : 'rel' num 0.75
 $ axis.minor.ticks.length.x       : NULL
 $ axis.minor.ticks.length.x.top   : NULL
 $ axis.minor.ticks.length.x.bottom: NULL
 $ axis.minor.ticks.length.y       : NULL
 $ axis.minor.ticks.length.y.left  : NULL
 $ axis.minor.ticks.length.y.right : NULL
 $ axis.minor.ticks.length.theta   : NULL
 $ axis.minor.ticks.length.r       : NULL
 $ axis.line                       : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ axis.line.x                     : NULL
 $ axis.line.x.top                 : NULL
 $ axis.line.x.bottom              : NULL
 $ axis.line.y                     : NULL
 $ axis.line.y.left                : NULL
 $ axis.line.y.right               : NULL
 $ axis.line.theta                 : NULL
 $ axis.line.r                     : NULL
 $ legend.background               : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.margin                   : 'margin' num [1:4] 5.5points 5.5points 5.5points 5.5points
  ..- attr(*, "unit")= int 8
 $ legend.spacing                  : 'simpleUnit' num 11points
  ..- attr(*, "unit")= int 8
 $ legend.spacing.x                : NULL
 $ legend.spacing.y                : NULL
 $ legend.key                      : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.key.size                 : 'simpleUnit' num 1.2lines
  ..- attr(*, "unit")= int 3
 $ legend.key.height               : NULL
 $ legend.key.width                : NULL
 $ legend.key.spacing              : 'simpleUnit' num 5.5points
  ..- attr(*, "unit")= int 8
 $ legend.key.spacing.x            : NULL
 $ legend.key.spacing.y            : NULL
 $ legend.frame                    : NULL
 $ legend.ticks                    : NULL
 $ legend.ticks.length             : 'rel' num 0.2
 $ legend.axis.line                : NULL
 $ legend.text                     :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : 'rel' num 0.8
  ..$ hjust        : NULL
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ legend.text.position            : NULL
 $ legend.title                    :List of 11
  ..$ family       : NULL
  ..$ face         : NULL
  ..$ colour       : NULL
  ..$ size         : NULL
  ..$ hjust        : num 0
  ..$ vjust        : NULL
  ..$ angle        : NULL
  ..$ lineheight   : NULL
  ..$ margin       : NULL
  ..$ debug        : NULL
  ..$ inherit.blank: logi TRUE
  ..- attr(*, "class")= chr [1:2] "element_text" "element"
 $ legend.title.position           : NULL
 $ legend.position                 : chr "right"
 $ legend.position.inside          : NULL
 $ legend.direction                : NULL
 $ legend.byrow                    : NULL
 $ legend.justification            : chr "center"
 $ legend.justification.top        : NULL
 $ legend.justification.bottom     : NULL
 $ legend.justification.left       : NULL
 $ legend.justification.right      : NULL
 $ legend.justification.inside     : NULL
 $ legend.location                 : NULL
 $ legend.box                      : NULL
 $ legend.box.just                 : NULL
 $ legend.box.margin               : 'margin' num [1:4] 0cm 0cm 0cm 0cm
  ..- attr(*, "unit")= int 1
 $ legend.box.background           : list()
  ..- attr(*, "class")= chr [1:2] "element_blank" "element"
 $ legend.box.spacing              : 'simpleUnit' num 11points
  ..- attr(*, "unit")= int 8
  [list output truncated]
 - attr(*, "class")= chr [1:2] "theme" "gg"
 - attr(*, "complete")= logi TRUE
 - attr(*, "validate")= logi TRUE
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Show the plot}
\NormalTok{scatter\_plot}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/unnamed-chunk-11-1.pdf}

}

\end{figure}

Our results are summarized in Table~\ref{tbl-modelresults}.

\hypertarget{tbl-modelresults}{}
\begin{table}
\caption{\label{tbl-modelresults}Explanatory models of flight time based on wing width and wing length }\tabularnewline

\centering
\begin{tabular}[t]{lc}
\toprule
  & Support Biden\\
\midrule
(Intercept) & \num{3.630}\\
 & (\num{0.307})\\
ABCYes & \num{0.468}\\
 & (\num{0.189})\\
CBSYes & \num{0.123}\\
 & \vphantom{1} (\num{0.209})\\
NBCYes & \num{0.056}\\
 & (\num{0.192})\\
CNNYes & \num{1.631}\\
 & (\num{0.209})\\
Fox\_NewsYes & \num{-3.128}\\
 & (\num{0.202})\\
MSNBCYes & \num{1.457}\\
 & (\num{0.242})\\
PBSYes & \num{0.681}\\
 & (\num{0.284})\\
OtherYes & \num{-1.218}\\
 & (\num{0.275})\\
TV\_typeNational Newscast & \num{-0.024}\\
 & (\num{0.218})\\
PartyIndependent & \num{-2.799}\\
 & (\num{0.267})\\
PartyOther & \num{-2.429}\\
 & (\num{0.465})\\
PartyRepublican & \num{-5.484}\\
 & (\num{0.306})\\
\midrule
Num.Obs. & \num{2500}\\
R2 & \num{0.786}\\
Log.Lik. & \num{-429.645}\\
ELPD & \num{-443.1}\\
ELPD s.e. & \num{26.9}\\
LOOIC & \num{886.1}\\
LOOIC s.e. & \num{53.8}\\
WAIC & \num{886.1}\\
RMSE & \num{0.22}\\
\bottomrule
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load necessary libraries}
\FunctionTok{library}\NormalTok{(car)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Loading required package: carData
\end{verbatim}

\begin{verbatim}

Attaching package: 'car'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:rstanarm':

    logit
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:dplyr':

    recode
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:purrr':

    some
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Check for multicollinearity using VIF}
\FunctionTok{vif}\NormalTok{(political\_preferences)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
             GVIF Df GVIF^(1/(2*Df))
ABC      1.135455  1        1.065577
CBS      1.213237  1        1.101471
NBC      1.104373  1        1.050891
CNN      1.185597  1        1.088851
Fox_News 1.223857  1        1.106281
MSNBC    1.151721  1        1.073183
PBS      1.069843  1        1.034332
Other    1.053979  1        1.026635
TV_type  1.226026  1        1.107260
Party    1.139090  3        1.021942
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# View the model summary}
\FunctionTok{summary}\NormalTok{(political\_preferences)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}

Model Info:
 function:     stan_glm
 family:       binomial [logit]
 formula:      voted_for_binary ~ ABC + CBS + NBC + CNN + Fox_News + MSNBC + 
       PBS + Other + TV_type + Party
 algorithm:    sampling
 sample:       4000 (posterior sample size)
 priors:       see help('prior_summary')
 observations: 2500
 predictors:   13

Estimates:
                           mean   sd   10%   50%   90%
(Intercept)               3.6    0.3  3.3   3.6   4.0 
ABCYes                    0.5    0.2  0.2   0.5   0.7 
CBSYes                    0.1    0.2 -0.2   0.1   0.4 
NBCYes                    0.1    0.2 -0.2   0.1   0.3 
CNNYes                    1.6    0.2  1.4   1.6   1.9 
Fox_NewsYes              -3.1    0.2 -3.4  -3.1  -2.9 
MSNBCYes                  1.5    0.2  1.1   1.5   1.8 
PBSYes                    0.7    0.3  0.3   0.7   1.1 
OtherYes                 -1.2    0.3 -1.6  -1.2  -0.9 
TV_typeNational Newscast  0.0    0.2 -0.3   0.0   0.3 
PartyIndependent         -2.8    0.3 -3.2  -2.8  -2.5 
PartyOther               -2.4    0.5 -3.0  -2.4  -1.8 
PartyRepublican          -5.5    0.3 -5.9  -5.5  -5.1

Fit Diagnostics:
           mean   sd   10%   50%   90%
mean_PPD 0.6    0.0  0.6   0.6   0.6

The mean_ppd is the sample average posterior predictive distribution of the outcome variable (for details see help('summary.stanreg')).

MCMC diagnostics
                         mcse Rhat n_eff
(Intercept)              0.0  1.0  3172 
ABCYes                   0.0  1.0  5909 
CBSYes                   0.0  1.0  5431 
NBCYes                   0.0  1.0  4506 
CNNYes                   0.0  1.0  4434 
Fox_NewsYes              0.0  1.0  4572 
MSNBCYes                 0.0  1.0  5086 
PBSYes                   0.0  1.0  4758 
OtherYes                 0.0  1.0  6239 
TV_typeNational Newscast 0.0  1.0  4652 
PartyIndependent         0.0  1.0  2557 
PartyOther               0.0  1.0  3566 
PartyRepublican          0.0  1.0  3317 
mean_PPD                 0.0  1.0  4896 
log-posterior            0.1  1.0  1750

For each parameter, mcse is Monte Carlo standard error, n_eff is a crude measure of effective sample size, and Rhat is the potential scale reduction factor on split chains (at convergence Rhat=1).
\end{verbatim}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{sec-first-point}{%
\subsection{First discussion point}\label{sec-first-point}}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\hypertarget{second-discussion-point}{%
\subsection{Second discussion point}\label{second-discussion-point}}

\hypertarget{third-discussion-point}{%
\subsection{Third discussion point}\label{third-discussion-point}}

\hypertarget{weaknesses-and-next-steps}{%
\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}}

Weaknesses and next steps should also be included.

\newpage

\appendix

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

\hypertarget{additional-data-details}{%
\section{Additional data details}\label{additional-data-details}}

\hypertarget{sec-model-details}{%
\section{Model details}\label{sec-model-details}}

\hypertarget{posterior-predictive-check}{%
\subsection{Posterior predictive
check}\label{posterior-predictive-check}}

In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
predictive check. This shows\ldots{}

In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
with the prior. This shows\ldots{}

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

Examining how the model fits, and is affected by, the data

}

\end{minipage}%

\caption{\label{fig-ppcheckandposteriorvsprior}\textbf{?(caption)}}

\end{figure}

\hypertarget{diagnostics}{%
\subsection{Diagnostics}\label{diagnostics}}

\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

Checking the convergence of the MCMC algorithm

}

\end{minipage}%

\caption{\label{fig-stanareyouokay}\textbf{?(caption)}}

\end{figure}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-post_dist-1.pdf}

}

\caption{\label{fig-post_dist}Posterior distribution for logistic
regression model}

\end{figure}

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-1.pdf}

}

}

\subcaption{\label{fig-trace1-1}Trace plot of Intercept}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-2.pdf}

}

}

\subcaption{\label{fig-trace1-2}Trace plot of race White}
\end{minipage}%
\newline
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-3.pdf}

}

}

\subcaption{\label{fig-trace1-3}Trace plot of race Black}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-4.pdf}

}

}

\subcaption{\label{fig-trace1-4}Trace plot of race Hispanic}
\end{minipage}%
\newline
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-5.pdf}

}

}

\subcaption{\label{fig-trace1-5}Trace plot of race Middle Eastern}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-6.pdf}

}

}

\subcaption{\label{fig-trace1-6}Trace plot of race Native American}
\end{minipage}%
\newline
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-7.pdf}

}

}

\subcaption{\label{fig-trace1-7}Trace plot of race Two or more races}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-8.pdf}

}

}

\subcaption{\label{fig-trace1-8}Trace plot of race Other}
\end{minipage}%
\newline
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace1-9.pdf}

}

}

\subcaption{\label{fig-trace1-9}Trace plot of Intercept}
\end{minipage}%

\caption{\label{fig-trace1}Trace plot of intercept and race}

\end{figure}

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace2-1.pdf}

}

}

\subcaption{\label{fig-trace2}Trace plot of region Northeast}
\end{minipage}%

\caption{\label{fig-trace2}Trace plot of region}

\end{figure}

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace3-1.pdf}

}

}

\subcaption{\label{fig-trace3-1}Trace plot of region Northeast}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace3-2.pdf}

}

}

\subcaption{\label{fig-trace3-2}Trace plot of region South}
\end{minipage}%
\newline
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-trace3-3.pdf}

}

}

\subcaption{\label{fig-trace3-3}Trace plot of region West}
\end{minipage}%

\caption{\label{fig-trace3}Trace plot of region}

\end{figure}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-rhat-1.pdf}

}

\caption{\label{fig-rhat}Rhat plot}

\end{figure}

\hypertarget{sec-credibility-interval}{%
\subsection{Credibility Interval}\label{sec-credibility-interval}}

Figure~\ref{fig-modelresults1} shows the 90\% credibility interval for
the model.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-modelresults1-1.pdf}

}

\caption{\label{fig-modelresults1}Credible intervals for predictors of
support for Biden}

\end{figure}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-citeR}{}}%
R Core Team. 2023. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-rohan}{}}%
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\end{CSLReferences}

\end{document}

### 2024-04-12 scripts/02-data_cleaning.R

@@ -80,7 +80,13 @@ cleaned_ces2020 <-
 #### Save data ####
 write_parquet(cleaned_ces2020, "data/analysis_data/cleaned_ces2020.parquet")
 
+head2020 <- head(cleaned_ces2020, 100)
 
+write_csv(head2020, "data/analysis_data/head2020.csv")
+
+
+row_count <- nrow(cleaned_ces2020)
+print(row_count)
 
 
 

### 2024-04-12 scripts/04-model.R

@@ -63,6 +63,10 @@ saveRDS(
 )
 
 
+head2020 <- head(ces2020_reduced, 100)
+
+write_csv(head2020, "data/analysis_data/head2020.csv")
+
 #test_file("scripts/05-test_class.R")
 #test_file("scripts/06-test_observations.R")
 #test_file("scripts/07-test_coefficients.R")

### 2024-04-16 paper/paper.qmd
fixes

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Media Matters/The Battle between Fake News and Fox News"
+subtitle: "Exploring the Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Voters from Different Parties"
 author: 
@@
 ---
-
 ```{r}
@@
 library(gridExtra)
+library(pander)
 
@@
 ```{r}
+#| include: false
+#| warning: false
+#| message: false
 ces2020 <-  read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
@@
 
+The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper.
+A reader should be able to read only the introduction and know what was done, why, and what was found.
+Likely 3 or 4 paragraphs, or 10 per cent of total.
+
 # Introduction
+The 2020 U.S.
+presidential election, between Republican candidate and incumbent President Donald Trump, and Democratic candidate and former Vice President Joe Biden, was one of the most intense in recent history.
+Trump's divisive and highly controversial statements while in office, as well as his administration's mishandling of the pandemic, widened the divide between the two parties during this election period.
+This division was also reflected in the media outlets favored by each party, with Fox News being known as the conservative media network highly favored by Republicans, while CNN leads as the Democrats' favorite.
+Often, media outlets on both sides presented differing narratives on the same events, with each side unwilling to concede.
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+The division of media was exacerbated by Trump's animosity against liberal networks.
+Trump famously labeled any unflattering issues that might work against him as "Fake News," regardless of their actual validity [@timm2020trump].
+He even handed out the "Fake News Award" through Twitter to several notable liberal media outlets, including CNN [@siddiqui2018trump].
+On the other hand, Democrats also have long-standing feuds with the Republican network Fox News.
+Biden has referred to Fox News as "one of the most destructive forces in the United States" [@stelter2022biden].
+With clear political alliances and agendas, these different media outlets might subtly influence their viewers' political ideology and voting decisions.
+Therefore, it is important to explore whether these media networks do indeed have influences on election outcomes and, if so, the magnitude of that effect.
+A good understanding of this relationship could enable voters to be more critical of the media they consume.
 
-The remainder of this paper is structured as follows. @sec-data....
+To explore and answer these questions, this paper analyzes the influence of watching specific media on voters' voting behavior.
+It uses the 2020 US election data from the Cooperative Election Study (CES), which surveys Americans before and after elections.
+From the dataset, information on voters' media preferences on America's most prominent networks, including ABC, CNN, Fox News, etc., was gathered.
+Then, a Bayesian logistic regression model was employed to estimate the election outcome between Trump and Biden based on voters' media preferences and their original party affiliation.
+The estimand of this paper is the actual number of people who supported Trump or Biden during the 2020 election.
+However, due to the difficulty of collecting data on millions of voters, this paper estimates the estimand using the logistic regression model trained using a sample from the CES dataset.
+The findings indicate that watching media networks with specific political ideologies is associated with higher chances of voting for the candidate they prefer.
+Among all networks, this relationship is most apparent in CNN and Fox News, exerting heavy influence on voters who classify as "Independent" or "Other." Additionally, this paper also studies the influence of watching national newscasts on voting outcomes compared to watching both national and local newscasts, finding no significant differences between the outcomes of the two.
 
-https://onlinelibrary.wiley.com/doi/full/10.1111/j.1467-9477.2011.00284.x
+The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model builds the model and discusses its justification and explanation, @sec-result highlights the results of the predictions using tables and graphs, and @sec-discussion contains discussions conducted based on the findings.
+These discussions address the voting prediction results based on TV types, party affiliation, and media influence, and discuss policy implications from the study.
 
@@
 
-Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat] and `kableExtra` [@citeKableExtra].
+Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat], `kableExtra` [@citeKableExtra], `arrow` [@citeArrow], `gridExtra` [@citeGridExtra], and `pander` [@citePander].
 
@@
 
-Data for this research comes from the 2020 Cooperative Election Study (CES) [@citeCes2020], a annual US political survey.
-The CES contains information about Americans' political view, voting behaviours and experiences across various political geography and social context.
+Data for this research comes from the 2020 Cooperative Election Study (CES) [@citeCes2020], an annual US political survey.
+The CES contains information about Americans' political views, voting behaviours and experiences across various political geography and social contexts.
 61,000 American adults participated in the survey in 2020.
@@
 
-Since this paper focuses on analyzing the influence of media usage on registered voters decision, I perform the following data cleaning process and selected the related variables.
-The dataset is cleaned by renaming the column names, changing the variable for from categorical to dummy, selecting the variables of interest, and filtering out missing information and information not related to the study.
-After cleaning, there are 10331 rows of data remain in the cleaned dataset.
+Since this paper focuses on analyzing the influence of media usage on registered voters' decisions, I performed the following data-cleaning process and selected the related variables.
+The dataset is cleaned by renaming the column names, changing the variable from categorical to dummy, selecting the variables of interest, and filtering out missing information and information not related to the study.
+After cleaning, there are 10331 rows of data remaining in the cleaned dataset.
 @tbl-clean-data shows a preview of the cleaned dataset.
@@
 And I filtered the responses in `presvote20post` to only "Biden" or "Trump" and converted the variable into a dummy variable where 1 represents "Biden" and 0 represents "Trump".
-Rest of the variable this paper focuses on are being divided into three categories: Media Use - Networks, Media Use - TV Type, and Party Affiliation.
+The rest of the variables this paper focuses on are being divided into three categories: Media Use - Networks, Media Use - TV Type, and Party Affiliation.
 
@@
 
-    -   This variable reports on what kind of TV news the respondent watches. A value of 1 signifies that the respondent watches "Local Newcast", 2 signifies "National Newscast"; 3 "Both".
+    -   This variable reports on what kind of TV news the respondent watches. A value of 1 signifies that the respondent only watches "Local Newcast", 2 signifies "National Newscast"; 3 "Both".
 
@@
 
-    -   This variable reports if the respondent political party affiliation.
-A value of 1 signifies that the respondent identifies as "Democrat", 2 signifies "Republican"; 3 "Independent", and 4 "Other".
+    -   This variable reports the respondent political party affiliation.
+A value of 1 signifies that the respondent identifies as "Democrat", 2 signifies "Republican"; 3 is "Independent", and 4 is "Other".
 
@@
 #| echo: false
+#| warning: false
 
+summary <- 
   ces2020 |>
   summary() |>
-  kable() |>
-  kable_styling()
+  kable()
+
+# Convert the summary to a data frame
+summary_df <- as.data.frame(summary)
+
+# Print the summary using pander
+pander(summary_df, style = "grid", split.tables = Inf)
 
@@
 It is evident that Biden has more supporters in this election.
-The seven listed media networks capture the majority networks people watch; while `Other` captures the rest.
-Due to the small number of respondents that only watch local newscast and missing values associated with this variable, the number of respondents that only watches local newscast becomes 0 after cleaning.
-Therefore, the value "Local Newscast" is excluded from later examinations and modelings.
-There are more respondents identifying as Democrat than than any other party.
-There are almost equal amount of Republicans and Independent voters; and only 534 voters identified as "Other."
+The seven listed media networks capture the majority of networks people watch; while `Other` captures the rest.
+Due to the conflict of "Local Newscast" with the variables for media use networks, the number of respondents that only watch local newscast becomes 0 after cleaning.
+If the respondent only watches local newscasts, then they would skip all the questions related to national newscasts (e.g.
+Do you watch ABC?) since these questions are not applicable.
+With no further media-related information for voters who only watch local newscasts, this value is excluded from later examinations and modelling.
+There are more respondents identifying as Democrats than any other party.
+There are almost equal amount of Republicans and Independent voters, and only 534 voters identified as "Other."
 
 ## Data Measurement
-
 Because the data was collected from surveys, there might be some inconsistencies and misinterpretations of the questions in people's responses.
-Therefore this section disects on what the variables are measuring.
-
-each of our variable is only representable for the following scenarios.
+Therefore this section discusses what the variables are measuring.
 
 Firstly, for the variable `votereg` indicating whether a respondent is registered to vote, the variable relies on self-reported information from survey respondents.
-Due to the inefficiencies of the US voter registration system, people who misunderstood their voter registration status might falsely reported their condition.
+Due to the inefficiencies of the US voter registration system, people who misunderstood their voter registration status might falsely report their condition.
 For example, some individuals might believe they reached the status simply because they are of age but did not actually register at their local office.
@@
 
-Representing the presidential candidate the respondent voted for, `CC20_410` takes into account of recall bias and social desirability bias along with people's reported presidential candidate preference.
+Representing the presidential candidate the respondent voted for, `CC20_410` considers recall bias, social desirability bias, and people's reported presidential candidate preference.
 Trump had made many controversial speeches throughout his presidency that contributed to his polarizing image and unpopularity in mainstream media.
@@
 
-People's media use networks is being represented by if  `ABC`, `CBS`, `NBC`, `CNN`, `Fox_News`, `MSNBC`, `PBS`, and `Other`.
+People's media use networks are represented by if  `ABC`, `CBS`, `NBC`, `CNN`, `Fox_News`, `MSNBC`, `PBS`, and `Other`.
 Relying on people's self-reported preferences, these variables are also subject to recall bias.
-Respondents might overestimate or underestimate their consumptions of certain network based on the content.
+Respondents might overestimate or underestimate their consumption of certain networks based on the content.
 They might only report the network which reported news that left a strong impression on them.
-In addition, respondents might choose to conceal their consumptions of certain media networks due to the network's political affiliation or reputation.
+In addition, respondents might choose to conceal their consumption of certain media networks due to the network's political affiliation or reputation.
 
-`TV_type` reports the respondents' preference in local newscast or national newscast (or both).
-The main concern over this variable lies in the fact that after data cleaning, the number of respondents exclusively watching local newscasts became zero due to missing values associated with this variable.
-The fact that many missing values are related to this variable could have unobservable implications that require future examinations.
-Therefore this study excludes the effect of only watching local newscast, and centers on people either only consume national newscast or both.
+`TV_type` reports the respondents' preference for local newscasts or national newscasts (or both).
+The main concern over this variable lies in the fact that voters who only watch local newscasts are filtered out of the dataset.
+Because filtering this value out is necessary for the examinations of the influence of other media networks, this study excludes the effect of only watching local newscasts and centers on people who either only consume national newscasts or both.
 
-The variable `Party` categories respondents into four categories.
+The variable `Party` categorizes respondents into four categories.
+"Democrat" means the voter identifies as a Democrat; "Republican" if the voter identifies themselves as a Republican.
+However, in this dataset, "Independent" is not affiliated with the American Independent Party; independent here means the voter has no party affiliation.
+Lastly, "Other" symbolizes the voter being part of a party that is neither Democratic nor Republican.
 Only having four categories might overlook the nuanced and diverse political beliefs held by individuals.
@@
 
-# Model
+# Model {@sec-model}
 
@@
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix - @sec-model-details].
 
@@
 
-I utilized a Bayesian logistic regression model to examine the relationship between voters' political preferences and their media use preferences.The model is formulated as follows:
+I utilized a Bayesian logistic regression model to examine the relationship between voters' political preferences and their media use preferences. The model is formulated as follows:
 
@@
 y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
-\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox_News}_i + \beta_6 \times \mbox{MSNBC}_i + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV_type}_i + \beta_{10} \times \mbox{Party}_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_5 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_6 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_7 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_8 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_9 &\sim \mbox{Normal}(0, 2.5) \\
-\beta_10 &\sim \mbox{Normal}(0, 2.5)
+\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i \nonumber \\
+&\quad + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox\_News}_i + \beta_6 \times \mbox{MSNBC}_i \nonumber \\
+&\quad + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV\_type}_i + \beta_{10} \times \mbox{Party}_i \nonumber \\
+\alpha &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_3 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_4 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_5 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_6 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_7 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_8 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_9 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_{10} &\sim \mbox{Normal}(0, 2.5) \nonumber
 \end{align}
@@
 The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_10$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively.
-Media use networks are being represented by the following predictor variables: \text{ABC}_i, \text{CBS}_i, \text{NBC}_i, \text{CNN}_i, \text{Fox_News}_i \text{MSNBC}_i ,\text{PBS}_i, and \text{Other}_i.
-The rest of the predictor variables are denoted as \text{TV_type}_i and \text{Party}_i, where $i$ indexes the individuals in the dataset.
+Media use networks are being represented by the following predictor variables:  \text{ABC}_i, \text{CBS}_i, \text{NBC}_i, \text{CNN}_i, \text{Fox\_News}_i, \text{MSNBC}_i, $\text{PBS}_i$, \text{Other}_i.
+The rest of the predictor variables are denoted as \text{TV\_type}_i and \text{Party}_i, where $i$ indexes the individuals in the dataset.
 
@@
 ### Model justification
+A positive relationship is expected between watching left-leaning (Democrat) media networks and voting for Biden, as well as a similar positive relationship between watching right-leaning (Republican) media networks and voting for Trump.
+According to @grieco2020americans, among the 7 networks identified in this study, Fox News is known as the most conservative media network, while CNN and MSNBC are leading liberal media outlets.
+Slightly leaning left, ABC, CBS, and NBC are generally considered neutral.
+PBS is also more liberal and Democratic-leaning, but not as extreme as CNN or MSNBC [@blake2014ranking].
+This assumption is grounded in findings that suggest exposure to media networks influences voters [@wettstein2017media].
 
-A positive relationship between watching left leaning (Democrat) media networks and voting for Biden; and a similar positive relationship between watching right leaning (Republican) media networks and voting for Trump.
-In particular, according to @grieco2020americans, among the 7 networks identified in this study, Fox News is known as the most conservative media network while CNN and MSNBC stand as leading liberal media.
-Slightly leaning left, ABC, CBS, and NBC are generally neutral.
-PBS is also more liberal and Democratic leaning, but not as extreme as CNN or MSNBC [@blake2014ranking].
-This is assumption is made based on the findings that state exposure to media network would have a influence on voter [@wettstein2017media].
-
-As most news and media outlets are more liberal leaning, I expect a slightly higher chance of voting for Biden for voters who watch both local and national newscasts.
-Local newscast might be more be perceived as more trustworthy and more community oriented; therefore, viewers may tend accept content and political opinions from local newscast more easily.
+As most news and media outlets are more liberal-leaning, I expect a slightly higher chance of voting for Biden for voters who watch both local and national newscasts.
+Local newscasts might be more be perceived as more trustworthy and more community-oriented; therefore, viewers may tend to accept content and political opinions from local newscasts more easily.
 On the other hand, voters who exclusively watch national news may adopt a more cautious approach and be less inclined to uncritically accept the material presented to them.
 Therefore, voters who watch both local and national newscasts might have a slightly higher chance of supporting Biden.
-
-In terms of the relationship of party affiliation and voting choices.
-There is an easy assumption; the majority of Democrat voters would vote for their candidate Biden, and almost all Republicans voting for Trump.
-I except a even voting outcomes from Independent and Other voters as they have not express their preferences between the two.
-
-In terms of the relationship between party affiliation and voting choices, it's reasonable to expect that the majority of Democrat voters would support their candidate, Biden, while a significant portion of Republican voters would favor Trump.
+In terms of the relationship between party affiliation and voting choices, it's reasonable to expect that the majority of Democrat voters would support their candidate, Biden, while a significant portion of Republican voters would favour Trump.
 This expectation is based on historical voting patterns and the ideological alignment between these parties and their respective candidates.
 However, it's less predictable how Independent and Other voters might vote, as they have not explicitly expressed their preferences between the two main candidates.
-Therefore, I anticipate half of the votes go to Biden and half to Trump.
+Therefore, I anticipate an equal split of votes between Biden and Trump for these two groups.
 
-```{r}
-
-ggplot(ces2020, aes(x = factor(voted_for), fill = PBS)) +
-  geom_bar(position = "dodge") +
-  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal()
-```
-
-# Results
+# Results {@sec-results}
 
 ## Data Results
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+# Function to extract legend from a ggplot object
+g_legend <- function(a.gplot) {
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)
+}
+
+```
 
@@
 #| message: false
-#| 
-# Create individual plots for each news channel
-plot_ABC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(ABC))) +
-  geom_bar(position = "dodge") +
-  labs(title = "ABC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() 
-  #guides(fill = FALSE)
 
-plot_CBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(CBS))) +
-  geom_bar(position = "dodge") +
-  labs(title = "CBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() #+
- # facet_wrap(~ ., ncol = 4) +
-  #guides(fill = FALSE)
-
-plot_NBC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(NBC))) +
-  geom_bar(position = "dodge") +
-  labs(title = "NBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() #+
- # facet_wrap(~ ., ncol = 4) +
-  #guides(fill = FALSE)
-
-plot_CNN <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(CNN))) +
-  geom_bar(position = "dodge") +
-  labs(title = "CNN", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal() #+
- # facet_wrap(~ ., ncol = 4) +
-  #guides(fill = FALSE)
-
-plot_Fox_News <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(Fox_News))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Fox News", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal()# +
-#  facet_wrap(~ ., ncol = 4) +
- # guides(fill = FALSE)
-
-plot_MSNBC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(MSNBC))) +
-  geom_bar(position = "dodge") +
-  labs(title = "MSNBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal()# +
-#  facet_wrap(~ ., ncol = 4) +
-  #guides(fill = FALSE)
-
-plot_PBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = PBS)) +
-  geom_bar(position = "dodge") +
-  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal()
-
-plot_Other <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(Other))) +
-  geom_bar(position = "dodge") +
-  labs(title = "Other", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
-  theme_minimal()# +
-  #guides(fill = FALSE)
-
-legend <- g_legend(plot_PBS + theme(legend.position='bottom'))
-
-grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS, plot_Other, legend, nrow = 3)
-
-#grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS + #theme(legend.position ='none'), plot_Other, legend, nrow = 3)
-
-```
-```{r, fig.height = 10, fig.width = 10}
-#| label: fig-network
-#| fig-cap: Distribution of Presidential Preferences by Network
-#| echo: false
-#| warning: false
-#| message: false
-# Create individual plots for each news channel
+#Create individual plots for each news channel
 plot_ABC <- ggplot(ces2020, aes(x = factor(ABC), fill = factor(voted_for))) +
@@
 
-@fig-network depicts the relationship between voters voting preference and media network preference.
-Because more voters voted for Biden, Biden supporters seem to watch more media network overall.
-Therefore, I examine the proportions of voters watching a specific network and voting for one of the two candidates.
-Biden supporters have a higher proportions of watching most networks.
-Among all the networks that have higher proportions of Biden voters, CNN and MSNBC, two of the most Democratic leaning news networks, have a significantly higher proportions of viewers that are Biden supporters and barely any viewers that support Trump.
-The only network that is being consumed by Trump supporters are Fox News, a network know to be Republican leaning.
-
-```{r, fig.height = 6.6, fig.width = 10}
-
-# Create individual plots for each news channel
-# plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post))) +
-#   geom_bar(position = "dodge") +
-#   labs(title = "Posted", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   theme(plot.title = element_text(hjust = 0.5)) +
-#   coord_cartesian(ylim = c(0, 4000)) +  
-#   guides(fill = FALSE)
-# 
-# plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment))) +
-#   geom_bar(position = "dodge") +
-#   labs(title = "Commented", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   coord_cartesian(ylim = c(0, 4000)) +  
-#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-#  # facet_wrap(~ ., ncol = 4) +
-#   guides(fill = FALSE)
-# 
-# plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read))) +
-#   geom_bar(position = "dodge") +
-#   labs(title = "Read", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   coord_cartesian(ylim = c(0, 4000)) +
-#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-#  # facet_wrap(~ ., ncol = 4) +
-#   guides(fill = FALSE)
-# 
-# plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow))) +
-#   geom_bar(position = "dodge") +
-#   labs(title = "Followed", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   coord_cartesian(ylim = c(0, 4000)) +
-#   theme(plot.title = element_text(hjust = 0.5)) +
-#  # facet_wrap(~ ., ncol = 4) +
-#   guides(fill = FALSE)
-# 
-# plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward))) +
-#   geom_bar(position = "dodge") +
-#   labs(title = "Forwarded", x = "Vote", y = "Count") +
-#   coord_cartesian(ylim = c(0, 4000)) +
-#   theme_minimal() +
-#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
-# 
-# 
-# legend <- g_legend(plot_forward + theme(legend.position='bottom', 
-#                                         legend.text = element_text(size = 15, face="bold"), 
-#                                         legend.title = element_blank()))
-# 
-# grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), legend, nrow = 2)
-
-```
-
-```{r}
-# Create individual plots for each news channel
-# plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post, levels = c("not_selected", "selected")))) +
-#   geom_bar(position = "stack", stat = "count") +
-#   labs(title = "Posted", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   theme(plot.title = element_text(hjust = 0.5)) +
-#   coord_cartesian(ylim = c(0, 6000)) +  
-#   guides(fill = FALSE)
-# 
-# plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment, levels = c("not_selected", "selected")))) +
-#   geom_bar(position = "stack", stat = "count") +
-#   labs(title = "Commented", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   coord_cartesian(ylim = c(0, 6000)) +  
-#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-#   guides(fill = FALSE)
-# 
-# plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read, levels = c("not_selected", "selected")))) +
-#   geom_bar(position = "stack", stat = "count") +
-#   labs(title = "Read", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   coord_cartesian(ylim = c(0, 6000)) +
-#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-#   guides(fill = FALSE)
-# 
-# plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow, levels = c("not_selected", "selected")))) +
-#   geom_bar(position = "stack", stat = "count") +
-#   labs(title = "Followed", x = "Vote", y = "Count") +
-#   theme_minimal() +
-#   coord_cartesian(ylim = c(0, 6000)) +
-#   theme(plot.title = element_text(hjust = 0.5)) +
-#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
-#   guides(fill = FALSE)
-# 
-# plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward, levels = c("not_selected", "selected")))) +
-#   geom_bar(position = "stack", stat = "count") +
-#   labs(title = "Forwarded", x = "Vote", y = "Count") +
-#   coord_cartesian(ylim = c(0, 6000)) +
-#   theme_minimal() +
-#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
-#  # facet_wrap(~ ., ncol = 4) +
-# 
-# 
-# #legend <- g_legend(plot_forward + theme(legend.position='bottom', 
-#                                         #legend.text = element_text(size = 15, face="bold"), 
-#                                        # legend.title = element_blank())
-# 
-# grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), nrow = 1)
-
-```
+@fig-network depicts the relationship between voters' voting preference and media network preference.
+Given that more voters supported Biden, it's evident that Biden supporters tend to watch more media networks overall.
+Consequently, I analyze the proportions of voters watching specific networks and their voting preferences.
+Biden supporters have higher proportions of watching most networks.
+Among all the networks that have higher proportions of Biden voters, CNN and MSNBC, two of the most Democratic-leaning news networks, have significantly higher proportions of viewers that are Biden supporters and barely any viewers that support Trump.
+The only network that is being consumed by Trump supporters is Fox News, a network known to be Republican-leaning.
 
@@
 @fig-party reports on the voting behaviours of voters from different parties.
-Democrat voters mostly voted for Biden, and Republicans for Trump unexpectely.
+Democrat voters mostly voted for Biden, and Republicans for Trump unexpectedly.
 The voting outcomes for Independent and Other voters are mostly even, with Biden collecting slightly more votes from the Independent voters.
@@
 ```
-@fig-foxnews and @fig-cnn take Fox News and CNN consumption into detail since they are the representation of Republican and Democratic network respectively.
-These two figures add in the respondents' party affiliation and examine if there is any differences in news consumption across different parties and their relationship with voting bahaviour.
+@fig-foxnews and @fig-cnn take Fox News and CNN consumption into detail since they are the representation of Republican and Democratic networks respectively.
+These two figures add in the respondents' party affiliation and examine if there are any differences in news consumption across different parties and their relationship with voting behaviour.
 
-For @fig-foxnews, almost all Democrat identifying respondents voted for Biden and the majority of them do not watch Fox News.
-Conversely, most Republicans voted for Trump and a high proportions of them watch Fox News.
-However, notably there are more Republicans who did not watch Fox News choosing to vote for Biden instead compared to their Democrat counterparts.
+For @fig-foxnews, almost all Democrat-identifying respondents voted for Biden and the majority of them do not watch Fox News.
+Conversely, most Republicans voted for Trump and a high proportion of them watch Fox News.
+However, notably, there are more Republicans who did not watch Fox News choosing to vote for Biden instead compared to their Democrat counterparts.
 The relationship becomes interesting when the respondents identify either as "Independent" or "Other." It appears that independent voters who watch Fox News have a higher likelihood of voting for Trump while those who do not are more likely to vote for Biden.
@@
 
-# Change labels for Fox_News variable
-
+{
   ggplot(ces2020, aes(x = CNN, fill = voted_for)) +
@@
     scale_fill_brewer(palette = "Set1")
+};
+
 ```
@@
 While most Democrat voters voted for Biden, the ones who do not watch CNN have a slightly higher chance of voting for Trump than the ones who do.
-Republicans who watch CNN also are more likely to vote for Biden compared to their counterparts that don't.
-The notable impact of network on Independent and Other voters is apparent as well.
+Republicans who watch CNN also are more likely to vote for Biden compared to their counterparts who don't.
+The notable impact of the network on Independent and Other voters is apparent as well.
 Independent voters who watch CNN are much more likely to vote for Biden while the ones that don't have a higher likelihood of voting for Trump.
 Others portray the same relationship.
-Because without the influence of media networks, the voting outcome for Indepdent and Other voters are almost evenly distributed between Biden and Trump, the results from the @fig-fox and @fig-cnn confirm the influence of media network on its viewers, and specifically its strong impact on viewers who neither are affiliated with the Democratic nor Republican party.
+Because without the influence of media networks, the voting outcome for independent and Other voters are almost evenly distributed between Biden and Trump, the results from the @fig-fox and @fig-cnn confirm the influence of media networks on its viewers, and specifically its strong impact on viewers who neither are affiliated with the Democratic nor Republican party.
 The political opinions of viewers who do not have a strong party affiliation could be easily influenced by their news consumption.
-
 ```{r}
@@
 
-scatter_plot <- ggplot(ces2020, aes(x = TV_type, fill = voted_for)) +
+{
+  print(
+    ggplot(ces2020, aes(x = TV_type, fill = voted_for)) +
       geom_bar() +
       facet_wrap(facets = vars(Party)) +
-  labs(title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
+      labs(
+        title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
         x = "TV Type",
         y = "Count",
-       color = "Voted for Biden (1) or Trump (0)") +
-  scale_fill_brewer(palette = "Set1")
- # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
+        color = "Voted for Biden (1) or Trump (0)"
+      ) +
+      scale_fill_brewer(palette = "Set1") +
       theme_minimal()
-
-# Show the plot
-scatter_plot
+  )
+}
 
@@
 
-The relationship between voters' TV news consumption and their political and voting preferences are depicted in @fig-tv.
-Unlike the apparent influence of specific networks, different TV consumption seem to have no significant influence on voters voting behaviour.
-Democrat voters generally voted for Biden regardless if they choose to only watch national newscast or watch both national and local newscast, the same for Republicans.
-For Independent and other voters, there is generally a even number of people who voted for Biden or Trump across the two groups of people that watch different newscast.
+```{r}
+# #| label: fig-tv
+# #| fig-cap: Relationship between TV News Consumption and Voting Behaviour by Party
+# #| echo: false
+# #| warning: false
+# #| message: false
+# 
+# ces2020$TV_type <- factor(ces2020$TV_type, labels = c("National & Local", "National"))
+# # 
+# ggplot(ces2020, aes(x = TV_type, fill = voted_for)) +
+#   geom_bar() +
+#   facet_wrap(facets = vars(Party)) +
+#   labs(title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
+#        x = "TV Type",
+#        y = "Count",
+#        color = "Voted for Biden (1) or Trump (0)") +
+#   scale_fill_brewer(palette = "Set1")
+#  # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
+#   theme_minimal()
+
+```
+
+The relationship between voters' TV news consumption and their political and voting preferences is depicted in @fig-tv.
+Unlike the apparent influence of specific networks, different TV consumption seems to have no significant influence on voters' voting behaviour.
+Democrat voters generally voted for Biden regardless if they chose to only watch national newscasts or watch both national and local newscasts, the same for Republicans.
+For Independent and other voters, there is generally an even number of people who voted for Biden or Trump across the two groups of people that watch different newscasts.
 
@@
 
-The results, summarized in @tbl-modelresults1, generally matches our expectation.
-To avoid multicollinearity, the model excluded the category "Both" from `TV_type` and "Party Democrat" from `Party.`The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels.
-In this case, the estimated log-odds of supporting Biden for individuals who do not watch any of these news networks, watches both national and local newscasts, and identify as a Democrat is 3.63.
+The results, summarized in @tbl-modelresults1, generally match our expectations.
+To avoid multicollinearity, the model excluded the category "Both" from `TV_type` and "Party Democrat" from `Party.`The intercept represents the estimated log odds of supporting Biden when all other predictors are held constant at their reference levels.
+In this case, the estimated log-odds of supporting Biden for individuals who do not watch any of these news networks watch both national and local newscasts and identify as a Democrat is 3.63.
 
-@fig-modelresults1 (see @sec-credibility-interval) shows range of coefficient estimates of our model within the 90% probability.
+@fig-modelresults1 (see @sec-credibility-interval) shows the range of coefficient estimates of our model within the 90% probability.
 The estimates are statistically significant if the intervals do not cross 0.
-The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
+The values for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
 
 Neutral networks (ABC, CBS, and NBC) only have a slight positive relationship with voting for Biden, and their results are all statistically insignificant as shown in @fig-modelresults1.
-Watching CNN is significantly positively correlated with voting for Biden; compared to the reference group, voter watching CNN on average increases the log-odds of them voting for Biden by 1.631 units.
-MSNBC also exhibits similar relationship, while PBS shows a slightly smaller but still positive relationship.
+Watching CNN is significantly positively correlated with voting for Biden; compared to the reference group, voters watching CNN on average increase the log-odds of them voting for Biden by 1.631 units.
+MSNBC also exhibits a similar relationship, while PBS shows a slightly smaller but still positive relationship.
 
-While only watching national newscast does decreases the likelihood of voting for Biden on a small scale compared to the reference group, there is no statistically significant relationship between the two.
+While only watching national newscasts does decreases the likelihood of voting for Biden on a small scale compared to the reference group, there is no statistically significant relationship between the two.
 Lastly, as expected, identifying as part of the Republican party substantially decreases the possibility of voting for Biden (estimated coefficient of -5.484).
@@
 
-```{r}
-# Load necessary libraries
-library(car)
+# Discussion {#sec-discussion}
 
-# Check for multicollinearity using VIF
-vif(political_preferences)
+## TV Types and Voting Choices
 
-# View the model summary
-summary(political_preferences)
+There seems to be no significant difference between the voting behaviours of voters who solely watch national newscasts and those who watch both local and national.
+This phenomenon can be attributed to the fact that nowadays, with advanced information technology and globalization, the materials from local newscasts might heavily overlap with those from national.
+Therefore watching local newscasts does not bring in additional new opinions or views.
+Moreover, factors such as individual preferences, demographics, and political affiliations may play a more significant role in shaping voting decisions than the specific type of news consumed.
+For example, individuals with strong partisan leanings may be more swayed by ideological alignment with a particular news network, regardless of whether it is local or national.
 
-```
+## Party Affiliation and Voting Choices
 
-# Discussion
+From both the data and modelling results, it is noticeable that Independent voters have a higher possibility of choosing Biden over Trump.
+This scenario is worth investigating as these voters belong neither to the Democratic party nor the Republican.
+Independent voters are usually divided between Democratic-leaning, Republican-leaning or no-leaning.
+These voters do not fully agree with the ideology of the party; therefore, they remain Independent.
+They tend to vote for whichever candidate whose belief most aligns with them [@zdanowicz2012neither].
+@pewresearch2019political analyzes the trend of Trump's job approval in his first two years in office and compares them with his precedents.
+While his ratings from Republican-leaning Independents are not significantly different from those of recent Presidents, his ratings from Democratic-leaning Independents were much lower than those of his predecessors.
+The ratings he received from them are as low as those from Democrats.
+The low ratings he received mainly stemmed from disagreements over the US-Mexican Wall, immigrants, and same-sex marriages.
+Many Independent voters report to have similar views on these subjects as the Democrats while Trump proposes very conservative views [@pewresearch2019political].
+During his later time in office, he has created more controversies regarding the COVID-19 pandemic that furthered distanced himself from the Independent voters.
+Many Independents are disappointed in his methods of handling the pandemic and proceeded to vote for Biden instead [@rosenbaum2020wealthy].
+And many of these voters vote for Biden tend to be correlated with their media consumption as discussed in the next section.
 
-## First discussion point {#sec-first-point}
+## Media Influence on Voting Behavior
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+The analysis reveals a clear correlation between media preferences and voting decisions.
+Viewers of left-leaning networks like CNN and MSNBC are more likely to vote for Biden, while those who watch right-leaning networks like Fox News tend to support Trump.
+The trend of Republicans gravitating towards Fox News and Democrats towards CNN can be attributed to several factors.
+Firstly, media outlets often tailor their content to align with the political leanings of their target audience.
+Fox News has positioned itself as a conservative-leaning network, catering to viewers who identify with Republican values and ideologies.
+Conversely, CNN has adopted a more liberal-leaning stance, appealing to viewers who align with Democratic principles.
 
-## Second discussion point
+Another factor contributing to this phenomenon is the presence of partisan echo chambers within media consumption.
+Republicans who watch Fox News are likely to encounter content that reinforces their existing beliefs and perspectives, creating a feedback loop that solidifies their support for conservative causes and candidates.
+Similarly, Democrats who tune into CNN may find their views validated and amplified, further strengthening their allegiance to liberal ideals and candidates.
 
-## Third discussion point
+Furthermore, the proliferation of political punditry and opinion-based programming on both networks plays a role in shaping viewer preferences.
+Fox News hosts like Sean Hannity and Tucker Carlson are known for their outspoken support of Republican policies and politicians, attracting conservative viewers who value their commentary.
+On the other hand, CNN features prominent personalities such as Anderson Cooper and Don Lemon, whose coverage often aligns with Democratic positions, resonating with liberal audiences.
 
-## Weaknesses and next steps
+The results highlight the partisan divide in media consumption, with Democrats favoring liberal-leaning networks and Republicans favoring conservative-leaning ones.
+This polarization in media consumption reflects broader political polarization in society and underscores the role of media as a driver of ideological divisions.
 
-Weaknesses and next steps should also be included.
+While the relationship of voter watching the network that supports his own party is straightforward, media networks have more complex impact on voters who do not belong to the two major parties.
+Independents who watch Fox News are more likely to vote for Trump than those who don't; and those who watch CNN are more likely to vote for Biden than those who don't.
+This fact further proves the assumption of the influence of media on voters, especially the "unbiased" ones.
+
+Additionally, the influence of left media network such as CNN on independent voters seem to be larger than that of right media such as Fox News.
+Independent voters who watch CNN has a higher likelihood of voting for Biden compared the Trump supporting rate from those who watches Fox News.
+There might be various explanations for this scenario.
+Firstly, other than Fox News, most of the main stream media networks are more or less pro Democrat.
+Therefore, independent voters on average would be more exposed to Democratic opinions and ideas if they spend time watching national news.
+In addition, as analyzed in the previous section, more Independents are liberal leaning; therefore, they are more likely to watch liberal news and vote for Biden .
+
+The relationship of media networks and Independent voters' votes suggests that media consumption plays a significant role in shaping political attitudes and voting behavior.
+This finding is highly useful for political figures who attempt to use media as an outlet to promote their campaigns and ideas.
+To maximize their votes, they should prioritize on using media platforms to attract voters who do not belong to the two major parties.
+By effectively utilizing these platforms, they can amplify their messages and policy proposals to resonate with independent voters who may not align strictly with either major party.
+Understanding the preferences and viewing habits of independent voters in relation to media consumption can inform targeted outreach and messaging strategies.
+Political campaigns can tailor their content and advertising efforts to align with the interests and concerns of independent voters, thereby increasing the likelihood of garnering their support.
+
+## Policy Implications
+
+The significant influence of media on political attitudes could be harmful to society if not regulated.
+Press and media with strong political leans are prone to misguide their audiences with tactiful words.
+In the past, there has been long histories where press selectively uses words like "slander" and "liar" to dismiss undirable statements and "honest" and "honerable" to defend people they support [@gentzkow2004rise].
+While this trend has been diminishing over decades, media's political standpoint are still discernable through their reports.
+Researchers at Carnegie Mellon University has found that the left and right media with opposite political views often use completely different words to describe the same idea [@knight2020left].
+Strategically phrasing their reports, they are able to turn the result in their favour.
+Therefore, there is a need for robust regulation to ensure accountability and accuracy in reporting.
+Policymakers may consider measures to promote transparency in media ownership, combat misinformation, and uphold journalistic standards
+It is important to educate voters in media literacy; they should be equipped with the skills to critically evaluate media sources, discern bias, and distinguish between factual reporting and opinion.
+
+## Weaknesses and Next Steps
+
+While clear correlation between voters' media preferences and their voting decision is discovered, the paper's main weakness lies in the fact that it does not address endogeneity issues, specifically reverse causality.
+Media consumption may not solely influence voting decisions; individuals predisposed to certain candidates may selectively consume media aligning with their existing beliefs.
+For example, Trump supporters may favor Fox News, while Biden supporters may prefer CNN.
+
+Additionally, the missing data in this study introduces inaccuracies in the findings.
+Despite starting with over 60,000 observations, only 10,000 remained after data cleaning.
+This loss of data, particularly in variables such as TV type, where the category "Local Newscast" was entirely eliminated, raises concerns about the representativeness of the sample.
+By excluding individuals who exclusively consume local news, I might overlook potentially significant insights into how their media consumption habits may influence voting behavior.
+
+In order to resolve endogeneity concerns, methods such as instrumental variable could be employed in the future to infer causality.
+More socioeconomic indicator controls such as income levels and education could be added to bring more understanding of voting dynamics.
+To observe the full influence of TV type on voting outcome, this variable has to be separated from the media variables in a separate model so that all three values of this variable can be examined.
 

### 2024-04-16 scripts/00-simulate_data.R

@@ -1,19 +1,105 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
+# Purpose: Simulates the US political support data
 # Author: Hannah Yu
-# Date: 8 April 2024 
+# Date: 8 April 2024
 # Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: --
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+# set seed
+set.seed(853)
+
+# Define the number of observations
+num_obs <- 1000
+
+# Simulate data for US political preferences
+simulate_us_vote <- 
+  tibble(
+    # Simulate random binary variables representing whether individuals watch each media network
+    ABC = sample(0:1, size = num_obs, replace = TRUE),
+    CBS = sample(0:1, size = num_obs, replace = TRUE),
+    NBC = sample(0:1, size = num_obs, replace = TRUE),
+    CNN = sample(0:1, size = num_obs, replace = TRUE),
+    Fox_News = sample(0:1, size = num_obs, replace = TRUE),
+    MSNBC = sample(0:1, size = num_obs, replace = TRUE),
+    PBS = sample(0:1, size = num_obs, replace = TRUE),
+    Other = sample(0:1, size = num_obs, replace = TRUE),
+    # Include Party variable representing political party affiliation
+    Party = sample(0:3, size = num_obs, replace = TRUE),
+    # Include TV_type variable representing type of TV news watched
+    TV_type = sample(0:2, size = num_obs, replace = TRUE),
+    # Calculate the probability of supporting Trump based on the sum of variables divided by 13
+    support_prob = ((ABC + CBS + NBC + CNN + Fox_News + MSNBC + PBS + Other + Party + TV_type) / 13), 
+  ) |>
+  mutate(
+    # Determine whether an individual supports Trump based on the calculated probability
+    support_biden = if_else(runif(n = num_obs) < support_prob, "yes", "no"),
[…]

### 2024-04-16 scripts/02-data_cleaning.R

@@ -30,8 +30,6 @@ raw_ces2020 <- read_parquet("data/raw_data/raw_ces2020.parquet", col_types = col
 ))
 
 
-
-
 # only interested in:
 # respondents who are registered to vote: votereg = 1
 # vote for Trump or Biden: CC20_410 = 1 Biden, 2 Trump
@@ -76,19 +74,6 @@ cleaned_ces2020 <-
   select(voted_for, ABC, CBS, NBC, CNN, Fox_News, MSNBC, PBS, Other, TV_type, Party)
 
 
-
 #### Save data ####
 write_parquet(cleaned_ces2020, "data/analysis_data/cleaned_ces2020.parquet")
-
-head2020 <- head(cleaned_ces2020, 100)
-
-write_csv(head2020, "data/analysis_data/head2020.csv")
-
-
-row_count <- nrow(cleaned_ces2020)
-print(row_count)
-
-
-
-
 

### 2024-04-16 scripts/03-test_data.R

@@ -1,15 +1,104 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Hannah Yu
-# Date: 8 April 2024 
+# Purpose: Tests the cleaned US CES 2020 data 
+# Author: Hannah
+# Date: 12 April 2024
 # Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: run 01-download_data.R and 02-data_cleaning.R first to
+# get the cleaned dataset
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(readr)
+
 
 #### Test data ####
+# read in cleaned data
+cleaned_ces2020 <-  read_parquet("data/analysis_data/cleaned_ces2020.parquet")
+
+
+# Check column class
+class(cleaned_ces2020$voted_for) == "factor"
+class(cleaned_ces2020$ABC) == "character"
+class(cleaned_ces2020$CBS) == "character"
+class(cleaned_ces2020$NBC) == "character"
+class(cleaned_ces2020$CNN) == "character"
+class(cleaned_ces2020$Fox_News) == "character"
+class(cleaned_ces2020$MSNBC) == "character"
+class(cleaned_ces2020$PBS) == "character"
+class(cleaned_ces2020$Other) == "character"
+class(cleaned_ces2020$TV_type) == "character"
+class(cleaned_ces2020$Party) == "character"
+
+# Range of data
+# Check range of data for voted_for  
+correct_voted_for <- 
+  c("Trump", "Biden")
+
+if (all(cleaned_ces2020$voted_for |>
+        unique() %in% correct_voted_for)) 
+{
+  "The cleaned voted_for match the expected voted_for"
+} else {
+  "Not all of the voted_for have been cleaned completely"
+}
+
+
+# Check range of data for tv
+correct_tv <-
+  c(
+    "Local Newscast",
+    "National Newscast",
+    "Both"
+  )
+
+if (all(cleaned_ces2020$TV_type |>
+        unique() %in% correct_tv)) 
+{
+  "The cleaned tv types match the expected tv types"
+} else {
+  "Not all of the tv types have been cleaned completely"
+}
+
+
+# Check range of data for party
+correct_party <-
+  c(
+    "Democrat",
+    "Republican",
+    "Independent",
+    "Other"
+  )
+
[…]

### 2024-04-16 scripts/04-model.R

@@ -33,7 +33,7 @@ analysis_data1$Party <- factor(analysis_data1$Party)
 # Create voted_for variable in binary form
 analysis_data1$voted_for_binary <- ifelse(analysis_data1$voted_for == "Biden", 1, 0)
 
-# Model  for n = 2000
+# Model  for n = 2500
 set.seed(853)
 
 ces2020_reduced <- 
@@ -63,20 +63,10 @@ saveRDS(
 )
 
 
-head2020 <- head(ces2020_reduced, 100)
+test_file("scripts/05-test_class.R")
+test_file("scripts/06-test_observations.R")
+test_file("scripts/07-test_coefficients.R")
 
-write_csv(head2020, "data/analysis_data/head2020.csv")
-
-#test_file("scripts/05-test_class.R")
-#test_file("scripts/06-test_observations.R")
-#test_file("scripts/07-test_coefficients.R")
-
-
-
-# Print unique values of tv_news24 and newspaper24 in the sliced sample
-print(unique(ces2020_reduced$TV_type))
-print(unique(ces2020_reduced$Newspaper_type))
-print(unique(analysis_data1$TV_type))
 
 
 

### 2024-04-16 scripts/05-test_class.R

@@ -1,0 +1,18 @@
+#### Preamble ####
+# Purpose: Tests the model class
+# Author: Hannah Yu
+# Date: 12 April 2024
+# Contact: realhananh.yu@mail.utoronto.ca
+# Pre-requisites: run 04-model.R to get model
+
+library("testthat")
+
+test_that("Check class", {
+  # Check if the model object inherits from any of the expected classes
+  expect_true(
+    inherits(political_preferences, "stanreg") ||
+      inherits(political_preferences, "glm") ||
+      inherits(political_preferences, "lm"),
+    info = "The class of political_preferences is as expected."
+  )
+})

### 2024-04-16 scripts/06-test_observations.R

@@ -1,0 +1,13 @@
+#### Preamble ####
+# Purpose: Tests the model number of observations
+# Author: Hannah Yu
+# Date: 12 April 2024
+# Contact: realhananh.yu@mail.utoronto.ca
+# Pre-requisites: run 04-model.R to get model
+
+test_that("Check number of observations is correct", {
+  # Check if the number of observations is equal to 2500
+  expect_equal(nrow(political_preferences$data), 2500,
+               info = "The number of observations is 2500"
+  )
+})

### 2024-04-16 scripts/07-test_coefficients.R

@@ -1,0 +1,12 @@
+#### Preamble ####
+# Purpose: Tests the model cofficient
+# Author: Hannah Yu
+# Date: 12 April 2024
+# Contact: realhananh.yu@mail.utoronto.ca
+# Pre-requisites: run 04-model.R to get model
+
+
+test_that("Check summary", {
+  summary_political <- summary(political_preferences)
+  expect_true("summary.stanreg" %in% class(summary_political))
+})

### 2024-04-17 paper/paper.qmd
fix

@@
   - Hannah Yu
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/hannahyu07/Fox-News"
 date: today
@@
 format: pdf
+toc: true
 number-sections: true
@@
 
-The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model builds the model and discusses its justification and explanation, @sec-result highlights the results of the predictions using tables and graphs, and @sec-discussion contains discussions conducted based on the findings.
+The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model builds the model and discusses its justification and explanation, @sec-results highlights the results of the predictions using tables and graphs, and @sec-discussion contains discussions conducted based on the findings.
 These discussions address the voting prediction results based on TV types, party affiliation, and media influence, and discuss policy implications from the study.
@@
 
-summary <- 
-  ces2020 |>
-  summary() |>
-  kable()
-
-# Convert the summary to a data frame
-summary_df <- as.data.frame(summary)
-
-# Print the summary using pander
-pander(summary_df, style = "grid", split.tables = Inf)
+ces2020 %>%
+  select(1:6) %>%
+  summary() %>%
+  kable() %>%
+  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
 
 ```
+```{r}
+#| message: false
+#| echo: false
+#| warning: false
+
+ces2020 %>%
+  select(7:11) %>%
+  summary() %>%
+  kable() %>%
+  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
+
+```
+
 @tbl-summary presents a summary of the cleaned data, showing detailed statistics about the dataset.
@@
 
-# Model {@sec-model}
+# Model {#sec-model}
 
@@
 
-# Results {@sec-results}
+# Results {#sec-results}
 
@@
       ) +
-      scale_fill_brewer(palette = "Set1") +
-      theme_minimal()
-  )
+      scale_fill_brewer(palette = "Set1")   )
 }

### 2024-04-18 paper/ces2020_datasheet.qmd
datasheet, more fix

---
title: "Datasheet for 2020 Cooperative Election Study"
subtitle: "The survey dataset used for 'The Battle between 'Fake News' and Fox News'"
author: 
  - Hannah Yu
thanks: "Code and data are available at: https://github.com/hannahyu07/Fox-News"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---
This datasheet is the extract of the questions from @gebru2021datasheets. And it was put together with the help of @citeRohan

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to study how Americans view Congress during elections, their voting behavior and experiences, and how these vary across different political and social contexts. The goal was to measure the distribution of voters' preferences across states [@citeCes2020]. For this study, this dataset satisfies all needs, and there was no specific gap that needed to be filled. 
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - This dataset is created by 60 research teams and organizations participating in the Cooperative Election Study (CES) initiative. 
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The creation of the dataset was funded by various sources, including the National Science Foundation which provided support for all even-year surveys from 2010 onward [@citeCes2020]. 
4. *Any other comments?*
    - No further comments.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance is 1 individual in the US who responded the CES2020 survey. 
2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 61,000 instances in total.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of all American adults, drawn using a sample matching methodology. The larger set would be the entire population of American adults. The sample is representative of the larger set in terms of demographic characteristics, as the matching process aimed to ensure similarity between the sample and the target population [@citeCes2020].
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of their demographic, income, education, political views, voting behaviours, and other relevant features. 
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No label or target association found. 
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- No, there is no missing information related to my research. 
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No explicit relationships available.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No recommended data splits available.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- There are no errors, sources of noise, or redundancies in the dataset. 
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained, will exist and remain constant over time. 
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Yes, this dataset identify sub-population traits including but not limited to age, gender, race, religion, political opinions, past/current voting choices, income, etc. 
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, the questions are generally not specific to the individual identification level. 
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- There are extensive questions over survey respondents' race, religion, political opinions, past/current voting choices, income, etc.
16. *Any other comments?*
	- No further comments.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- All data were acquired through survey.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Survey respondents respond to these questions through means including smartphones, laptops, and tabloids,
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset is a sample drawn using YouGov's matched random sample methodology. The sampling strategy involves selecting a random sample from the target population and then matching each member of the target sample to one or more matching members from a pool of opt-in respondents using proximity matching [@citeCes2020].
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The individuals involved in the data collection process include American adults who participated in the survey. Compensation details, such as whether respondents were compensated and the amount, are not provided in the information provided.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Data was collected twice. The pre-election questionnaires were distributed from September 29 to November 2, 2020; the post-election questionnaires from November 8 to December 14, 2020. This timeframe match the creation timeframe of the data associated with the instances.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected from Harvard Dataverse https://doi.org/10.7910/DVN/E9N6PH. I downloaded through library `dataverse` [@citeDataverse] from R Programming Language [@citeR].
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Yes, survey respondents answered the surveys willingly. 
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Yes, survey respondents answered the surveys willingly knowing that their data will be used. 
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- No
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
12. *Any other comments?*
	- No further comments.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- I only selected the columns I need and removed all missing observations from the columns. The columns are "votereg," "CC20_410," "cc20_300a," "cc20_300c," "cc20_300b_1," "cc20_300b_2," "cc20_300b_3," "cc20_300b_4,"  "cc20_300b_5," "cc20_300b_6,"  "cc20_300b_7," "cc20_300b_8," and "CC20_433a."
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The "raw" data was saved; it can be access through https://doi.org/10.7910/DVN/E9N6PH 
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The software used is R Programming Language @citeR.
4. *Any other comments?*
	- No further comments.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, this dataset was made public by the researchers; therefore it has been widely used for many purposes. 
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No
3. *What (other) tasks could the dataset be used for?*
	- More election prediction could be performed using the dataset. 
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- As this dataset was collected in 2020, using it to predict future elections might not be appropriate. 
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- There are no tasks for which the dataset should not be used.
6. *Any other comments?*
	- No further comments.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is available via the URL link from Harvard Dataverse. Any company, institution, or organization could access it through the link. 
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- It is available via the URL link https://doi.org/10.7910/DVN/E9N6PH. 
3. *When will the dataset be distributed?*
	- Data release 1 happened in March 26, 2021.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No
7. *Any other comments?*
	- No further comments.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Harvard Dataverse is responsible for supporting the dataset. 
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- There is a contact us button in the Harvard Dataverse website where user could message Dataverse. 
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- No, the final version has been released on the website, and it would not be updated. 
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- No
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset is still available via Harvard Dataset. 
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- No, this dataset was put together by 60 research teams each with theirn own Principal Invigilators. It is designed to sample American adults during the 2020 election. Therefore it can not be extended. 
8. *Any other comments?*
	- No further comments.

\newpage

# References

### 2024-04-18 paper/paper.qmd
datasheet, more fix

@@
 ---
-title: "Media Matters/The Battle between Fake News and Fox News"
+title: "The Battle between 'Fake News' and Fox News"
 subtitle: "Exploring the Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Voters from Different Parties"
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study examines the impact of media consumption on voting behavior in the 2020 U.S.
+presidential election with data from the Cooperative Election Study (CES 2020).
+Using logistic regression, I analyze the relationship between watching specific media networks and voting for either Trump or Biden among individuals with varying political affiliations.
+The analysis shows that viewing political leaning networks have a significant impact on voting preferences among Democrats, Republicans, and Independents, with CNN viewers more likely to support Biden and Fox News viewers favoring Trump.
+The findings that among voters from all parties, Independent voters' supports are heavily determined by their preferred media emphasize media's role in shaping electoral outcomes and the importance of promoting media literacy and addressing challenges created by media polarization"
 format: pdf
@@
 library(gridExtra)
-library(pander)
-
+#library(pander)
 #library(cowplot)
@@
 # Model {#sec-model}
-
-The goal of our modelling strategy is twofold. Firstly,...
 
@@
 
-The analysis reveals a clear correlation between media preferences and voting decisions.
+There is a clear correlation between media preferences and voting decisions.
 Viewers of left-leaning networks like CNN and MSNBC are more likely to vote for Biden, while those who watch right-leaning networks like Fox News tend to support Trump.
-The trend of Republicans gravitating towards Fox News and Democrats towards CNN can be attributed to several factors.
-Firstly, media outlets often tailor their content to align with the political leanings of their target audience.
-Fox News has positioned itself as a conservative-leaning network, catering to viewers who identify with Republican values and ideologies.
-Conversely, CNN has adopted a more liberal-leaning stance, appealing to viewers who align with Democratic principles.
+The trend can be explained by media outlets tailoring their content to align with the political leanings of their target audience.
+As a conservative network catering to Republican viewers, Fox News hosts like Sean Hannity and Tucker Carlson are known for their outspoken support of Republican policies and politicians.
+Conversely, to appeal to their Democrat viewers, CNN features prominent liberal personalities such as Anderson Cooper.
+Additionally, increased viewing of content with political implications might further reinforce the viewers' beliefs.
+For example, Republicans watching Fox News often encounter content that reinforces their conservative beliefs, solidifying their support for right-wing causes and candidates.
 
-Another factor contributing to this phenomenon is the presence of partisan echo chambers within media consumption.
-Republicans who watch Fox News are likely to encounter content that reinforces their existing beliefs and perspectives, creating a feedback loop that solidifies their support for conservative causes and candidates.
-Similarly, Democrats who tune into CNN may find their views validated and amplified, further strengthening their allegiance to liberal ideals and candidates.
+While the impact of media on the Republicans and Democrats is fairly straightforward, media networks have a more complex impact on voters who do not belong to the two major parties.
+Independents who watch Fox News are more likely to vote for Trump than those who don't, and those who watch CNN are more likely to vote for Biden than those who don't.
+This fact further proves the assumption of the influence of media on voters, especially the "unbiased" ones.
+The influence of left media networks such as CNN on independent voters seems to be larger than that of right media such as Fox News.
+Independent voters who watch CNN have a higher likelihood of voting for Biden compared to the Trump-supporting rate from those who watch Fox News.
+There might be various explanations for this scenario.
+Firstly, other than Fox News, most of the mainstream media networks are more or less pro-Democrat.
+Therefore, independent voters on average would be more exposed to Democratic opinions and ideas if they spend time watching national news.
+In addition, as analyzed in the previous section, more Independents are liberal-leaning; therefore, they are more likely to watch liberal news and vote for Biden.
 
-Furthermore, the proliferation of political punditry and opinion-based programming on both networks plays a role in shaping viewer preferences.
-Fox News hosts like Sean Hannity and Tucker Carlson are known for their outspoken support of Republican policies and politicians, attracting conservative viewers who value their commentary.
-On the other hand, CNN features prominent personalities such as Anderson Cooper and Don Lemon, whose coverage often aligns with Democratic positions, resonating with liberal audiences.
-
-The results highlight the partisan divide in media consumption, with Democrats favoring liberal-leaning networks and Republicans favoring conservative-leaning ones.
-This polarization in media consumption reflects broader political polarization in society and underscores the role of media as a driver of ideological divisions.
-
-While the relationship of voter watching the network that supports his own party is straightforward, media networks have more complex impact on voters who do not belong to the two major parties.
-Independents who watch Fox News are more likely to vote for Trump than those who don't; and those who watch CNN are more likely to vote for Biden than those who don't.
-This fact further proves the assumption of the influence of media on voters, especially the "unbiased" ones.
-
-Additionally, the influence of left media network such as CNN on independent voters seem to be larger than that of right media such as Fox News.
-Independent voters who watch CNN has a higher likelihood of voting for Biden compared the Trump supporting rate from those who watches Fox News.
-There might be various explanations for this scenario.
-Firstly, other than Fox News, most of the main stream media networks are more or less pro Democrat.
-Therefore, independent voters on average would be more exposed to Democratic opinions and ideas if they spend time watching national news.
-In addition, as analyzed in the previous section, more Independents are liberal leaning; therefore, they are more likely to watch liberal news and vote for Biden .
-
-The relationship of media networks and Independent voters' votes suggests that media consumption plays a significant role in shaping political attitudes and voting behavior.
-This finding is highly useful for political figures who attempt to use media as an outlet to promote their campaigns and ideas.
-To maximize their votes, they should prioritize on using media platforms to attract voters who do not belong to the two major parties.
-By effectively utilizing these platforms, they can amplify their messages and policy proposals to resonate with independent voters who may not align strictly with either major party.
-Understanding the preferences and viewing habits of independent voters in relation to media consumption can inform targeted outreach and messaging strategies.
-Political campaigns can tailor their content and advertising efforts to align with the interests and concerns of independent voters, thereby increasing the likelihood of garnering their support.
+The relationship between media networks and Independent voters' votes suggests that media consumption plays a significant role in shaping political attitudes and voting behaviour.
+This finding is highly useful for political figures who attempt to use media to promote their campaigns and ideas.
+To increase the likelihood of being supported by Independent voters, politicians use media platforms to attract them and deliver messages and policy proposals that resonate with them.
 
@@
 The significant influence of media on political attitudes could be harmful to society if not regulated.
-Press and media with strong political leans are prone to misguide their audiences with tactiful words.
-In the past, there has been long histories where press selectively uses words like "slander" and "liar" to dismiss undirable statements and "honest" and "honerable" to defend people they support [@gentzkow2004rise].
-While this trend has been diminishing over decades, media's political standpoint are still discernable through their reports.
-Researchers at Carnegie Mellon University has found that the left and right media with opposite political views often use completely different words to describe the same idea [@knight2020left].
+Press and media with strong political leans are prone to misguide their audiences with tactful words.
+In the past, there have been long histories where the press selectively uses words like "slander" and "liar" to dismiss undesirable statements and "honest" and "honourable" to defend people they support [@gentzkow2004rise].
+While this trend has been diminishing over decades, the media's political standpoint is still noticeable through their reports.
+Researchers at Carnegie Mellon University have found that the left and right media with opposite political views often use completely different words to describe the same idea [@knight2020left].
 Strategically phrasing their reports, they are able to turn the result in their favour.
-Therefore, there is a need for robust regulation to ensure accountability and accuracy in reporting.
-Policymakers may consider measures to promote transparency in media ownership, combat misinformation, and uphold journalistic standards
-It is important to educate voters in media literacy; they should be equipped with the skills to critically evaluate media sources, discern bias, and distinguish between factual reporting and opinion.
+Therefore, policymakers may consider making regulations to ensure accountability and accuracy in reporting.
+It is equally important to educate voters in media literacy; they should be equipped with the skills to critically evaluate media sources, discern bias, and distinguish between factual reporting and opinion.
 
@@
 
-While clear correlation between voters' media preferences and their voting decision is discovered, the paper's main weakness lies in the fact that it does not address endogeneity issues, specifically reverse causality.
+While a clear correlation between voters' media preferences and their voting decisions is discovered, the paper's main weakness lies in the fact that it does not address endogeneity issues, specifically reverse causality.
 Media consumption may not solely influence voting decisions; individuals predisposed to certain candidates may selectively consume media aligning with their existing beliefs.
-For example, Trump supporters may favor Fox News, while Biden supporters may prefer CNN.
+For example, Trump supporters may favour Fox News, while Biden supporters may prefer CNN.
 
@@
 This loss of data, particularly in variables such as TV type, where the category "Local Newscast" was entirely eliminated, raises concerns about the representativeness of the sample.
-By excluding individuals who exclusively consume local news, I might overlook potentially significant insights into how their media consumption habits may influence voting behavior.
+By excluding individuals who exclusively consume local news, I might overlook potentially significant insights into how their media consumption habits may influence voting behaviour.
 
-In order to resolve endogeneity concerns, methods such as instrumental variable could be employed in the future to infer causality.
+In order to resolve endogeneity concerns, methods such as instrumental variables could be employed in the future to infer causality.
 More socioeconomic indicator controls such as income levels and education could be added to bring more understanding of voting dynamics.
-To observe the full influence of TV type on voting outcome, this variable has to be separated from the media variables in a separate model so that all three values of this variable can be examined.
+To observe the full influence of TV type on the voting outcome, this variable has to be separated from the media variables in a separate model so that all three values of this variable can be examined.
 

### 2024-04-18 scripts/replications.R

@@ -1,19 +1,0 @@
-#### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Hannah Yu
-# Date: 8 April 2024 
-# Contact: realhannah.yu@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-library(tidyverse)
-# [...UPDATE THIS...]
-
-#### Load data ####
-# [...ADD CODE HERE...]
-
-
-

### 2024-04-18 paper/Fake News vs Fox News.qmd
more fixes, add graphs.

--- 2024-04-18 paper/paper.qmd
@@
 ---
-title: "The Battle between 'Fake News' and Fox News"
+title: "Fake News vs Fox News"
 subtitle: "Exploring the Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Voters from Different Parties"
@@
 library(gridExtra)
-#library(pander)
+library(dataverse)
 #library(cowplot)
@@
 
-Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat], `kableExtra` [@citeKableExtra], `arrow` [@citeArrow], `gridExtra` [@citeGridExtra], and `pander` [@citePander].
+Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat], `kableExtra` [@citeKableExtra], `arrow` [@citeArrow], `gridExtra` [@citeGridExtra], and `dataverse` [@citeDataverse].
 
@@
 #| label: fig-party
-#| fig-cap: Relationship between TV News Consumption and Voting Behaviour by Party
+#| fig-cap: Relationship between Party Affiliation and Voting Behaviour 
 #| echo: false
@@
 Others portray the same relationship.
-Because without the influence of media networks, the voting outcome for independent and Other voters are almost evenly distributed between Biden and Trump, the results from the @fig-fox and @fig-cnn confirm the influence of media networks on its viewers, and specifically its strong impact on viewers who neither are affiliated with the Democratic nor Republican party.
+Because without the influence of media networks, the voting outcome for independent and Other voters are almost evenly distributed between Biden and Trump, the results from the @fig-foxnews and @fig-cnn confirm the influence of media networks on its viewers, and specifically its strong impact on viewers who neither are affiliated with the Democratic nor Republican party.
 The political opinions of viewers who do not have a strong party affiliation could be easily influenced by their news consumption.
@@
 }
-
-```
-
-```{r}
-# #| label: fig-tv
-# #| fig-cap: Relationship between TV News Consumption and Voting Behaviour by Party
-# #| echo: false
-# #| warning: false
-# #| message: false
-# 
-# ces2020$TV_type <- factor(ces2020$TV_type, labels = c("National & Local", "National"))
-# # 
-# ggplot(ces2020, aes(x = TV_type, fill = voted_for)) +
-#   geom_bar() +
-#   facet_wrap(facets = vars(Party)) +
-#   labs(title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
-#        x = "TV Type",
-#        y = "Count",
-#        color = "Voted for Biden (1) or Trump (0)") +
-#   scale_fill_brewer(palette = "Set1")
-#  # scale_color_manual(values = c("red", "blue")) +  # Customize colors for better visibility
-#   theme_minimal()
 
@@
 
-The results, summarized in @tbl-modelresults1, generally match our expectations.
+The results, summarized in @tbl-modelresults, generally match our expectations.
 To avoid multicollinearity, the model excluded the category "Both" from `TV_type` and "Party Democrat" from `Party.`The intercept represents the estimated log odds of supporting Biden when all other predictors are held constant at their reference levels.
@@
 
-# Additional data details
-
 # Model details {#sec-model-details}
@@
 ## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-#pp_check(first_model) +
- # theme_classic() +
- # theme(legend.position = "bottom")
-
-#posterior_vs_prior(first_model) +
-  #theme_minimal() +
- # scale_color_brewer(palette = "Set1") +
- # theme(legend.position = "bottom") +
- # coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-#plot(first_model, "trace")
-
-#plot(first_model, "rhat")
-```
 
@@
 ```
+In @fig-post_dist, a posterior distribution is implemented.
+This compares who people voted for in reality with the prediction results from the posterior distribution from the logistic regression model.
+This posterior distribution fitting perfectly with the actual data suggests that the my logistic model is a good representation of the actual voting preferences in the 2020 election data.
 
@@
 
-#### Read data ####
-# analysis_data1 <- read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
-
-# Convert variables to factors
-#analysis_data$race <- factor(analysis_data$race)
-#analysis_data$region <- factor(analysis_data$region)
-#analysis_data$employ <- factor(analysis_data$employ)
+analysis_data <- read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
 
 # Create voted_for variable in binary form
-# analysis_data1$voted_for_binary <- ifelse(analysis_data1$voted_for == "Biden", 1, 0)
-# 
-# # Model 1 for n = 1000
-# set.seed(853)
-# 
-# ces2020_reduced <- 
-#   analysis_data1 |> 
-#   slice_sample(n = 2500)
-# 
-# posterior_vs_prior(political_preferences, size = 0.3) +
-#   theme_minimal() +
-#   theme(legend.position = "bottom") +
-#   theme(axis.text.x=element_text(hjust=1, vjust=0.5),
-#         text=element_text(size=8)) +
-#   coord_flip()
+analysis_data$voted_for_binary <- ifelse(analysis_data$voted_for == "Biden", 1, 0)
+
+set.seed(853)
+
+ces2020_reduced <- 
+  analysis_data |> 
+  slice_sample(n = 2500)
+
+posterior_vs_prior(political_preferences, size = 0.3) +
+   theme_minimal() +
+   theme(legend.position = "bottom") +
+   theme(axis.text.x=element_text(hjust=1, vjust=0.5),
+         text=element_text(size=8)) +
+   coord_flip()
 ```
+@fig-post_prior compares the prior distribution of parameters with the posterior distribution of parameters in my logistic regression model.
+The majority of the model parameters do not vary much even after data are taken into account.
+This shows that the observed data matches with the initial belief and expectation about the voting preferences for 2020 presidential election.
+
+## Markov chain Monte Carlo Convergence Check
 
@@
 #| label: fig-trace1
-#| fig-cap: "Trace plot of intercept and race"
-#| fig-subcap: ["Trace plot of Intercept", "Trace plot of race White", "Trace plot of race Black", "Trace plot of race Hispanic", "Trace plot of race Middle Eastern", "Trace plot of race Native American", "Trace plot of race Two or more races", "Trace plot of race Other"]
-#| layout-ncol: 2
+#| fig-cap: "Trace plot of Intercept and Media Type"
+#| fig-subcap: ["Trace plot of Intercept", "Trace plot of ABC Yes", "Trace plot of CBS Yes", "Trace plot of race NBC Yes", "Trace plot of race CNN Yes", "Trace plot of Fox_News Yes", "Trace plot of MSNBC Yes", "Trace plot of PBS Yes", "Trace plot of Other Yes"]
+#| layout-ncol: 3
 
-#plot(political_preferences1, "trace")
 plot(political_preferences, "trace", "(Intercept)")
-
 plot(political_preferences, "trace", "ABCYes")
@@
 #| label: fig-trace2
-#| fig-cap: "Trace plot of region"
-#| fig-subcap: ["Trace plot of region Northeast", "Trace plot of region South", "Trace plot of region West"]
+#| fig-cap: "Trace plot of TV Type"
+#| fig-subcap: ["Trace plot of TV_type National Newscast"]
 #| layout-ncol: 2
@@
 plot(political_preferences, "trace", "TV_typeNational Newscast")
+
 ```
@@
 #| label: fig-trace3
-#| fig-cap: "Trace plot of region"
-#| fig-subcap: ["Trace plot of region Northeast", "Trace plot of region South", "Trace plot of region West"]
+#| fig-cap: "Trace plot of Party"
+#| fig-subcap: ["Trace plot of Party Independent", "Trace plot of Party Other", "Trace plot of Party Republican"]
 #| layout-ncol: 2
@@
 
+@fig-trace1, @fig-trace2, @fig-trace3 are the trace plot of the model.
+The lines are horizontal and oscillating, and have overlaps between the chains, suggesting no existing signs of issues with the model.
+
+@fig-rhat is the Rhat plot of the model.
+It compares the variability within each chain to the variability between chains in MCMC.
+In ideal condition, the Rhat should be close to 1, indicating that the chains have converged to the same distribution.
+This Rhat plot is indeed close to 1, suggesting that the MCMC algorithm has reached convergence for the model.
+
 ## Credibility Interval {#sec-credibility-interval}

### 2024-04-18 paper/ces2020_datasheet.qmd
more fixes, add graphs.

@@
 title: "Datasheet for 2020 Cooperative Election Study"
-subtitle: "The survey dataset used for 'The Battle between 'Fake News' and Fox News'"
+subtitle: "The survey dataset used for 'Fake News vs Fox News'"
 author: 

### 2024-04-18 scripts/02-data_cleaning.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
+# Purpose: Cleans the raw plane data 
 # Author: Hannah Yu
 # Date: 8 April 2024 
 # Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 01-download_data.R
-# Any other information needed?  dropped none
+# Any other information needed? 
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-04-18 scripts/04-model.R

@@ -26,7 +26,6 @@ analysis_data1$MSNBC <- factor(analysis_data1$MSNBC)
 analysis_data1$PBS <- factor(analysis_data1$PBS)
 analysis_data1$Other <- factor(analysis_data1$Other)
 analysis_data1$TV_type <- factor(analysis_data1$TV_type)
-#analysis_data1$Newspaper_type <- factor(analysis_data1$Newspaper_type)
 analysis_data1$Party <- factor(analysis_data1$Party)
 
 
@@ -39,7 +38,6 @@ set.seed(853)
 ces2020_reduced <- 
   analysis_data1 |> 
   slice_sample(n = 2500)
-print(unique(ces2020_reduced$TV_type))
 
 write.csv(ces2020_reduced, file = "reduced_ces2020.csv")
 

### 2024-04-18 paper/Fake News vs Fox News.qmd
fix abstract

@@
 title: "Fake News vs Fox News"
-subtitle: "Exploring the Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Voters from Different Parties"
+subtitle: "The Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Party Voters"
 author: 
@@
 date-format: long
-abstract: "This study examines the impact of media consumption on voting behavior in the 2020 U.S.
+abstract: "This study examines the impact of media consumption on voting behaviour in the 2020 U.S.
 presidential election with data from the Cooperative Election Study (CES 2020).
-Using logistic regression, I analyze the relationship between watching specific media networks and voting for either Trump or Biden among individuals with varying political affiliations.
-The analysis shows that viewing political leaning networks have a significant impact on voting preferences among Democrats, Republicans, and Independents, with CNN viewers more likely to support Biden and Fox News viewers favoring Trump.
-The findings that among voters from all parties, Independent voters' supports are heavily determined by their preferred media emphasize media's role in shaping electoral outcomes and the importance of promoting media literacy and addressing challenges created by media polarization"
+Using logistic regression, I analyze the relationship between watching specific media networks and voting for either Trump or Biden among Democrat, Republican, Independent, and Other voters.
+The analysis shows that viewing political-leaning networks significantly impacts voting preferences among voters from all party backgrounds, with CNN viewers more likely to support Biden and Fox News viewers favouring Trump.
+The findings highlight the media’s role in shaping electoral outcomes, especially its influence on Independent voters, and the importance of addressing challenges posed by media polarization."
 format: pdf
@@
 library(dataverse)
-#library(cowplot)
-#library(lemon)
+
 ```
@@
 
-The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper.
-A reader should be able to read only the introduction and know what was done, why, and what was found.
-Likely 3 or 4 paragraphs, or 10 per cent of total.
-
 # Introduction
@@
 presidential election, between Republican candidate and incumbent President Donald Trump, and Democratic candidate and former Vice President Joe Biden, was one of the most intense in recent history.
-Trump's divisive and highly controversial statements while in office, as well as his administration's mishandling of the pandemic, widened the divide between the two parties during this election period.
-This division was also reflected in the media outlets favored by each party, with Fox News being known as the conservative media network highly favored by Republicans, while CNN leads as the Democrats' favorite.
-Often, media outlets on both sides presented differing narratives on the same events, with each side unwilling to concede.
+Trump's many highly controversial statements while in office and his administration's mishandling of the pandemic widened the divide between the two parties during this election period.
+This division was reflected in the media outlets favored by each party, with Fox News being known as the conservative media network highly favored by Republicans, while CNN leads as the Democrats' favorite.
 
 The division of media was exacerbated by Trump's animosity against liberal networks.
-Trump famously labeled any unflattering issues that might work against him as "Fake News," regardless of their actual validity [@timm2020trump].
+Trump famously labeled any unflattering issues that might work against him as "Fake News" [@timm2020trump].
 He even handed out the "Fake News Award" through Twitter to several notable liberal media outlets, including CNN [@siddiqui2018trump].
@@
 Biden has referred to Fox News as "one of the most destructive forces in the United States" [@stelter2022biden].
-With clear political alliances and agendas, these different media outlets might subtly influence their viewers' political ideology and voting decisions.
+With clear political alliances, these different media outlets might subtly influence their viewers' political ideology and voting decisions using their content.
 Therefore, it is important to explore whether these media networks do indeed have influences on election outcomes and, if so, the magnitude of that effect.
@@
 To explore and answer these questions, this paper analyzes the influence of watching specific media on voters' voting behavior.
-It uses the 2020 US election data from the Cooperative Election Study (CES), which surveys Americans before and after elections.
-From the dataset, information on voters' media preferences on America's most prominent networks, including ABC, CNN, Fox News, etc., was gathered.
-Then, a Bayesian logistic regression model was employed to estimate the election outcome between Trump and Biden based on voters' media preferences and their original party affiliation.
+It uses the 2020 US election data from the Cooperative Election Study (CES), which surveys Americans before and after elections @citeCes2020.
+From the dataset, I gathered information on voters' media preferences on America's most prominent networks, including ABC, CNN, Fox News, etc.
+Then, I used a Bayesian logistic regression model to estimate the election outcome between Trump and Biden based on voters' media preferences and their original party affiliation.
 The estimand of this paper is the actual number of people who supported Trump or Biden during the 2020 election.
@@
 61,000 American adults participated in the survey in 2020.
+This dataset is favoured over other available datasets because of its large observation numbers and wide-ranging information collected from the respondents.
 
@@
 ces2020[1:5, 1:11] |>
-  kable()
+  kable(booktabs = TRUE, linesep = "")
 ```
@@
   summary() %>%
-  kable() %>%
+  kable(booktabs = TRUE, linesep = "") %>%
   kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
@@
 ```
+
 ```{r}
@@
 Lastly, "Other" symbolizes the voter being part of a party that is neither Democratic nor Republican.
-Only having four categories might overlook the nuanced and diverse political beliefs held by individuals.
+Only having four categories might overlook the diverse political beliefs held by individuals.
 Some may have hybrid or unconventional political views that don't fit neatly into these categories.
@@
 
-# Model {#sec-model}
+## Data Analysis
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix - @sec-model-details].
-
-## Model set-up
-
-I utilized a Bayesian logistic regression model to examine the relationship between voters' political preferences and their media use preferences. The model is formulated as follows:
-
-\begin{align}
-y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
-\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i \nonumber \\
-&\quad + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox\_News}_i + \beta_6 \times \mbox{MSNBC}_i \nonumber \\
-&\quad + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV\_type}_i + \beta_{10} \times \mbox{Party}_i \nonumber \\
-\alpha &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_1 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_2 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_3 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_4 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_5 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_6 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_7 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_8 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_9 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
-\beta_{10} &\sim \mbox{Normal}(0, 2.5) \nonumber
-\end{align}
-
-In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump).
-The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_10$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively.
-Media use networks are being represented by the following predictor variables:  \text{ABC}_i, \text{CBS}_i, \text{NBC}_i, \text{CNN}_i, \text{Fox\_News}_i, \text{MSNBC}_i, $\text{PBS}_i$, \text{Other}_i.
-The rest of the predictor variables are denoted as \text{TV\_type}_i and \text{Party}_i, where $i$ indexes the individuals in the dataset.
-
-The intercept and coefficients are assigned informative prior distributions to regularize the model.
-Specifically, a normal distribution with a mean of 0 and a standard deviation of 2.5 for each parameter is assumed.
-
-This modeling approach is chosen for several reasons.
-Firstly, logistic regression is well-suited for binary outcome variables, making it appropriate for analyzing voting behavior.
-Additionally, Bayesian methods enables the incorporation of prior knowledge and uncertainty into our analysis, which provides more robust estimates of the model parameters.
-Alternative modeling approaches, such as linear regression models, were also considered.
-However, Bayesian logistic regression is chosen to fit the resulting binary variable of voter's decision.
-
-We run the model in R [@citeR] using the `rstanarm` package of [@citeRstanarm].
-We use the default priors from `rstanarm`.
-Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters.
-To avoid excessive runtime, we randomly sampled 2500 observations to fit the model.
-Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see Appendix @sec-model-details).
-
-### Model justification
-A positive relationship is expected between watching left-leaning (Democrat) media networks and voting for Biden, as well as a similar positive relationship between watching right-leaning (Republican) media networks and voting for Trump.
-According to @grieco2020americans, among the 7 networks identified in this study, Fox News is known as the most conservative media network, while CNN and MSNBC are leading liberal media outlets.
-Slightly leaning left, ABC, CBS, and NBC are generally considered neutral.
-PBS is also more liberal and Democratic-leaning, but not as extreme as CNN or MSNBC [@blake2014ranking].
-This assumption is grounded in findings that suggest exposure to media networks influences voters [@wettstein2017media].
-
-As most news and media outlets are more liberal-leaning, I expect a slightly higher chance of voting for Biden for voters who watch both local and national newscasts.
-Local newscasts might be more be perceived as more trustworthy and more community-oriented; therefore, viewers may tend to accept content and political opinions from local newscasts more easily.
-On the other hand, voters who exclusively watch national news may adopt a more cautious approach and be less inclined to uncritically accept the material presented to them.
-Therefore, voters who watch both local and national newscasts might have a slightly higher chance of supporting Biden.
-In terms of the relationship between party affiliation and voting choices, it's reasonable to expect that the majority of Democrat voters would support their candidate, Biden, while a significant portion of Republican voters would favour Trump.
-This expectation is based on historical voting patterns and the ideological alignment between these parties and their respective candidates.
-However, it's less predictable how Independent and Other voters might vote, as they have not explicitly expressed their preferences between the two main candidates.
-Therefore, I anticipate an equal split of votes between Biden and Trump for these two groups.
-
-# Results {#sec-results}
-
-## Data Results
 ```{r}
@@
   theme_minimal()+
-  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+  theme(plot.title = element_text(hjust = 0.5)) +
+  theme(legend.position="none")
 
@@
   theme_minimal()+
-  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+  theme(plot.title = element_text(hjust = 0.5))+  
+  theme(legend.position="none")
 
@@
   theme_minimal()+
-  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+  theme(plot.title = element_text(hjust = 0.5))+
+  theme(legend.position="none")
 
@@
   theme_minimal()+
-  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally
+  theme(plot.title = element_text(hjust = 0.5))+
+  theme(legend.position="none")
 
-plot_PBS <- ggplot(ces2020, aes(x = factor(PBS, levels = c("Yes", "No")), fill = voted_for)) +
+plot_PBS <- ggplot(ces2020, aes(x = factor(PBS, levels = c("Yes", "No")), fill = "Voted for")) +
   geom_bar(position = "dodge") +
@@
 ```
-
 @fig-network depicts the relationship between voters' voting preference and media network preference.
@@
 
-## Model Results
+# Model {#sec-model}
+
+## Model set-up
+
+I utilized a Bayesian logistic regression model to examine the relationship between voters' political preferences and their media use preferences. The model is formulated as follows:
+
+\begin{align}
+y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
+\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i \nonumber \\
+&\quad + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox\_News}_i + \beta_6 \times \mbox{MSNBC}_i \nonumber \\
+&\quad + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV\_type}_i + \beta_{10} \times \mbox{Party}_i \nonumber \\
+\alpha &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_3 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_4 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_5 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_6 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_7 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_8 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_9 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_{10} &\sim \mbox{Normal}(0, 2.5) \nonumber
+\end{align}
+
+In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump).
+The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_10$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively.
+Media use networks are being represented by the following predictor variables:  $\text{ABC}_i$, $\text{CBS}_i$, $\text{NBC}_i$, $\text{CNN}_i$, $\text{Fox\_News}_i$, $\text{MSNBC}_i$, $\text{PBS}_i$, $\text{Other}_i$.
+The rest of the predictor variables are denoted as $\text{TV\_type}_i$ and $\text{Party}_i$, where $i$ indexes the individuals in the dataset.
+
+The intercept and coefficients are assigned informative prior distributions to regularize the model.
+Specifically, a normal distribution with a mean of 0 and a standard deviation of 2.5 for each parameter is assumed.
+
+This modeling approach is chosen for several reasons.
+Firstly, logistic regression is well-suited for binary outcome variables, making it appropriate for analyzing voting behavior.
+Additionally, Bayesian methods enables the incorporation of prior knowledge and uncertainty into the analysis, which provides more robust estimates of the model parameters.
+Alternative modeling approaches, such as linear regression models, were also considered.
+However, Bayesian logistic regression is chosen to fit the resulting binary variable of voter's decision.
+
+I run the model in R [@citeR] using the `rstanarm` package of [@citeRstanarm].
+I use the default priors from `rstanarm`.
+Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters.
+I randomly sampled 2500 observations to fit the model to avoid excessive run time.
+
+### Model justification
+A positive relationship is expected between watching left-leaning (Democrat) media networks and voting for Biden, as well as a similar positive relationship between watching right-leaning (Republican) media networks and voting for Trump.
+According to @grieco2020americans, among the 7 networks identified in this study, Fox News is known as the most conservative media network, while CNN and MSNBC are leading liberal media outlets.
+Slightly leaning left, ABC, CBS, and NBC are generally considered neutral.
+PBS is also more liberal and Democratic-leaning, but not as extreme as CNN or MSNBC [@blake2014ranking].
+This assumption is grounded in findings that suggest exposure to media networks influences voters [@wettstein2017media].
+
+As most news and media outlets are more liberal-leaning, I expect a slightly higher chance of voting for Biden for voters who watch both local and national newscasts.
+Local newscasts might be more be perceived as more trustworthy and more community-oriented; therefore, viewers may tend to accept content and political opinions from local newscasts more easily.
+On the other hand, voters who exclusively watch national news may adopt a more cautious approach and be less inclined to uncritically accept the material presented to them.
+Therefore, voters who watch both local and national newscasts might have a slightly higher chance of supporting Biden.
+In terms of the relationship between party affiliation and voting choices, it's reasonable to expect that the majority of Democrat voters would support their candidate, Biden, while a significant portion of Republican voters would favour Trump.
+This expectation is based on historical voting patterns and the ideological alignment between these parties and their respective candidates.
+However, it's less predictable how Independent and Other voters might vote, as they have not explicitly expressed their preferences between the two main candidates.
+Therefore, I anticipate an equal split of votes between Biden and Trump for these two groups.
+
+# Results {#sec-results}
+
 ```{r}
@@
 
-The results, summarized in @tbl-modelresults, generally match our expectations.
+The results, summarized in @tbl-modelresults, generally match the expectations.
 To avoid multicollinearity, the model excluded the category "Both" from `TV_type` and "Party Democrat" from `Party.`The intercept represents the estimated log odds of supporting Biden when all other predictors are held constant at their reference levels.
@@
 Identifying as Independent or Other voters have no statistically significant influence on voting behaviours.
+
+Model diagnostics, including convergence checks and posterior summaries, and explanations can be found in Appendix @sec-model-details.
 

### 2024-04-18 scripts/02-data_cleaning.R

@@ -5,7 +5,6 @@
 # Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 01-download_data.R
-# Any other information needed? 
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-04-19 paper/Fake News vs Fox News.qmd
update llm, delete unwanted sketches, small edits

@@
 
-Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat], `kableExtra` [@citeKableExtra], `arrow` [@citeArrow], `gridExtra` [@citeGridExtra], and `dataverse` [@citeDataverse].
+Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@rstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat], `kableExtra` [@citeKableExtra], `arrow` [@citeArrow], `gridExtra` [@citeGridExtra], and `dataverse` [@citeDataverse].
 
@@
 For example, some individuals might believe they reached the status simply because they are of age but did not actually register at their local office.
-According to @inaccurate, there are millions of voter registrations that are no longer valid or inaccurate.
+According to @inaccurate, there are millions of voter registrations that are innaccurate or no longer valid.
 
@@
   scale_fill_manual(values = c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme(plot.title = element_text(hjust = 0.5)) +
   theme_minimal()+
-  theme(plot.title = element_text(hjust = 0.5)) +
   theme(legend.position="none")
@@
 
-plot_PBS <- ggplot(ces2020, aes(x = factor(PBS, levels = c("Yes", "No")), fill = "Voted for")) +
+plot_PBS <- ggplot(ces2020, aes(x = factor(PBS, levels = c("Yes", "No")), fill = voted_for)) +
   geom_bar(position = "dodge") +
@@
   theme(plot.title = element_text(hjust = 0.5)) +
-  theme(legend.position="none")
+  theme(legend.position="none")+
+  labs(fill = "Voted for")
 
@@
 
-I run the model in R [@citeR] using the `rstanarm` package of [@citeRstanarm].
+I run the model in R [@citeR] using the `rstanarm` package of [@rstanarm].
 I use the default priors from `rstanarm`.
@@
 In the past, there have been long histories where the press selectively uses words like "slander" and "liar" to dismiss undesirable statements and "honest" and "honourable" to defend people they support [@gentzkow2004rise].
-While this trend has been diminishing over decades, the media's political standpoint is still noticeable through their reports.
+While this trend has been diminishing over the years, the media's political standpoint is still noticeable through their reports.
 Researchers at Carnegie Mellon University have found that the left and right media with opposite political views often use completely different words to describe the same idea [@knight2020left].
@@
 Therefore, policymakers may consider making regulations to ensure accountability and accuracy in reporting.
-It is equally important to educate voters in media literacy; they should be equipped with the skills to critically evaluate media sources, discern bias, and distinguish between factual reporting and opinion.
+It is equally important to educate voters in media literacy; they should be equipped with the skills to critically evaluate media sources and distinguish between factual reporting and opinion.
 
@@
 While a clear correlation between voters' media preferences and their voting decisions is discovered, the paper's main weakness lies in the fact that it does not address endogeneity issues, specifically reverse causality.
-Media consumption may not solely influence voting decisions; individuals predisposed to certain candidates may selectively consume media aligning with their existing beliefs.
-For example, Trump supporters may favour Fox News, while Biden supporters may prefer CNN.
+Media consumption may not solely influence voting decisions; individuals favouring certain candidates may selectively consume media aligning with their existing beliefs.
+For example, instead of watching Fox News making people to support Trump, people might watch Fox News because they already support Trump and the things Fox News stands for.
 

### 2024-04-19 paper/Fake News vs Fox News.qmd
updated abstract, graph titles, small changes

@@
 date-format: long
-abstract: "This study examines the impact of media consumption on voting behaviour in the 2020 U.S.
-presidential election with data from the Cooperative Election Study (CES 2020).
-Using logistic regression, I analyze the relationship between watching specific media networks and voting for either Trump or Biden among Democrat, Republican, Independent, and Other voters.
+abstract: "Media consumption causes major impacts on the voting behvaior of a population base, with the most influential example being visible in the 2020 US presidential elections.
+Using logistic regression and data from the Cooperative Election Study (CES 2020), I analyze the relationship between watching specific media networks and voting for either Trump or Biden among Democrat, Republican, Independent, and Other voters.
 The analysis shows that viewing political-leaning networks significantly impacts voting preferences among voters from all party backgrounds, with CNN viewers more likely to support Biden and Fox News viewers favouring Trump.
@@
 presidential election, between Republican candidate and incumbent President Donald Trump, and Democratic candidate and former Vice President Joe Biden, was one of the most intense in recent history.
-Trump's many highly controversial statements while in office and his administration's mishandling of the pandemic widened the divide between the two parties during this election period.
+Trump's many controversial statements while in office and his administration's mishandling of the pandemic widened the divide between the two parties during this election period.
 This division was reflected in the media outlets favored by each party, with Fox News being known as the conservative media network highly favored by Republicans, while CNN leads as the Democrats' favorite.
@@
   summary() %>%
-  kable(booktabs = TRUE, linesep = "") %>%
+  kable(booktabs = TRUE, linesep = "" ) %>%
   kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

### 2024-04-19 paper/Fake_News_vs_Fox_News.qmd
last minute changes, small edit over wording and graph titles

--- 2024-04-19 paper/Fake News vs Fox News.qmd
@@
 date-format: long
-abstract: "Media consumption causes major impacts on the voting behvaior of a population base, with the most influential example being visible in the 2020 US presidential elections.
+abstract: "Media consumption has a notable impact on voting behaviour, with the most influential example in the 2020 US presidential elections.
 Using logistic regression and data from the Cooperative Election Study (CES 2020), I analyze the relationship between watching specific media networks and voting for either Trump or Biden among Democrat, Republican, Independent, and Other voters.
@@
 The division of media was exacerbated by Trump's animosity against liberal networks.
-Trump famously labeled any unflattering issues that might work against him as "Fake News" [@timm2020trump].
+Trump famously labelled any unflattering issues that might work against him as "Fake News" [@timm2020trump].
 He even handed out the "Fake News Award" through Twitter to several notable liberal media outlets, including CNN [@siddiqui2018trump].
@@
 With clear political alliances, these different media outlets might subtly influence their viewers' political ideology and voting decisions using their content.
-Therefore, it is important to explore whether these media networks do indeed have influences on election outcomes and, if so, the magnitude of that effect.
+Therefore, it is important to explore whether these media networks have influences on election outcomes and, if so, the magnitude of that effect.
 A good understanding of this relationship could enable voters to be more critical of the media they consume.
@@
 To explore and answer these questions, this paper analyzes the influence of watching specific media on voters' voting behavior.
-It uses the 2020 US election data from the Cooperative Election Study (CES), which surveys Americans before and after elections @citeCes2020.
+It uses the 2020 US election data from the Cooperative Election Study (CES), which surveys Americans before and after elections [@citeCes2020].
 From the dataset, I gathered information on voters' media preferences on America's most prominent networks, including ABC, CNN, Fox News, etc.
@@
 
-Data for this research comes from the 2020 Cooperative Election Study (CES) [@citeCes2020], an annual US political survey.
+Data for this research comes from the 2020 Cooperative Election Study (CES), an annual US political survey [@citeCes2020].
 The CES contains information about Americans' political views, voting behaviours and experiences across various political geography and social contexts.
@@
 Among all the networks that have higher proportions of Biden voters, CNN and MSNBC, two of the most Democratic-leaning news networks, have significantly higher proportions of viewers that are Biden supporters and barely any viewers that support Trump.
-The only network that is being consumed by Trump supporters is Fox News, a network known to be Republican-leaning.
+The only network that is being heavily consumed by Trump supporters is Fox News, a network known to be Republican-leaning.
 
@@
   facet_wrap(facets = vars(Party)) +
-  labs(title = "Relationship Between Party Affiliation and Voting Behaviour",
+  labs(
        x = "Vote",
@@
   facet_wrap(facets = vars(Party)) +
-  labs(title = "Relationship between Fox News Consumption and Voting Behavior by Party",
+  labs(
        x = "Fox News",
@@
     facet_wrap(facets = vars(Party)) +
-    labs(title = "Relationship between CNN Consumption and Voting Behaviour by Party",
+    labs(
          x = "CNN",
@@
       labs(
-        title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
+
         x = "TV Type",
@@
 In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump).
-The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_10$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively.
+The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_{10}$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively.
 Media use networks are being represented by the following predictor variables:  $\text{ABC}_i$, $\text{CBS}_i$, $\text{NBC}_i$, $\text{CNN}_i$, $\text{Fox\_News}_i$, $\text{MSNBC}_i$, $\text{PBS}_i$, $\text{Other}_i$.
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Explanatory Models for Political Preferences (n = 2500)"
 #| warning: false

### 2024-04-19 paper/Fake_News_vs_Fox_News.qmd
special thanks addition, and other small fixes

@@
   - Hannah Yu
-thanks: "Code and data are available at: https://github.com/hannahyu07/Fox-News"
+thanks: "Code and data are available at: https://github.com/hannahyu07/Fox-News.
+Special thanks to my dear friends Luca Carnegie and Chaitanya Khamar for their love and support; this paper would not have been done so beautifully without your generous help and ideas.
+Special thanks for Rohan Alexander for his wonderful help and continual support.
+"
 date: today
@@
 The 2020 U.S.
-presidential election, between Republican candidate and incumbent President Donald Trump, and Democratic candidate and former Vice President Joe Biden, was one of the most intense in recent history.
-Trump's many controversial statements while in office and his administration's mishandling of the pandemic widened the divide between the two parties during this election period.
-This division was reflected in the media outlets favored by each party, with Fox News being known as the conservative media network highly favored by Republicans, while CNN leads as the Democrats' favorite.
+presidential election, between Republican President Donald Trump, and Democratic candidate Joe Biden, was one of the most intense in recent history.
+This was especially due to the large polarization in political opinion among Americans.
+This was especially reflected in the media outlets favored by Americans, with Fox News being commonly known as the news network highly favored by Republicans, and Cable News Network (CNN) being commonly known as the Democrats' favorite.
 
-The division of media was exacerbated by Trump's animosity against liberal networks.
+Throughout his presidency and re-election campaign, Trump held noticeable animosity against liberal networks.
 Trump famously labelled any unflattering issues that might work against him as "Fake News" [@timm2020trump].
 He even handed out the "Fake News Award" through Twitter to several notable liberal media outlets, including CNN [@siddiqui2018trump].
-On the other hand, Democrats also have long-standing feuds with the Republican network Fox News.
-Biden has referred to Fox News as "one of the most destructive forces in the United States" [@stelter2022biden].
-With clear political alliances, these different media outlets might subtly influence their viewers' political ideology and voting decisions using their content.
-Therefore, it is important to explore whether these media networks have influences on election outcomes and, if so, the magnitude of that effect.
-A good understanding of this relationship could enable voters to be more critical of the media they consume.
+Democrats also have long-standing issues with the Republican news networks like Fox News.
+For instance, Joe Biden has referred to Fox News as "one of the most destructive forces in the United States" [@stelter2022biden].
+With certain networks having clear political alliances, these different media outlets could influence their viewers' political ideologies and voting decisions.
+Consequently, it is important to explore whether US media networks have had significant influences on election outcomes.
+Understanding this could give a  good understanding of this relationship could enable voters to be more critical of the media they consume.
 
-To explore and answer these questions, this paper analyzes the influence of watching specific media on voters' voting behavior.
+I analyze the influence of specific media on voters' voting behavior.
 It uses the 2020 US election data from the Cooperative Election Study (CES), which surveys Americans before and after elections [@citeCes2020].
@@
 Then, I used a Bayesian logistic regression model to estimate the election outcome between Trump and Biden based on voters' media preferences and their original party affiliation.
-The estimand of this paper is the actual number of people who supported Trump or Biden during the 2020 election.
+
+The estimand of this paper is the probability of people voting Biden during the 2020 election based on news channel viewership.
 However, due to the difficulty of collecting data on millions of voters, this paper estimates the estimand using the logistic regression model trained using a sample from the CES dataset.
+
 The findings indicate that watching media networks with specific political ideologies is associated with higher chances of voting for the candidate they prefer.
-Among all networks, this relationship is most apparent in CNN and Fox News, exerting heavy influence on voters who classify as "Independent" or "Other." Additionally, this paper also studies the influence of watching national newscasts on voting outcomes compared to watching both national and local newscasts, finding no significant differences between the outcomes of the two.
+This is most apparent in with CNN and Fox News, who are shown to exert heavy influence on voters identifying as "Independent" or "Other.".
+Watching local news over these national networks appears to have no significant effect on the probability of voting for Trump or Biden, as well.
 
-The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model builds the model and discusses its justification and explanation, @sec-results highlights the results of the predictions using tables and graphs, and @sec-discussion contains discussions conducted based on the findings.
-These discussions address the voting prediction results based on TV types, party affiliation, and media influence, and discuss policy implications from the study.
+The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model describes, justifies, and explains my model, @sec-results highlights the results of the predictions using tables and graphs, and @sec-discussion contains important implications and conclusions based on the findings.
 
@@
 
-The dependent variable of my examination is: `presvote20post`, renamed to `voted_for`.
+The dependent variable is: `presvote20post`, renamed to `voted_for`.
 This variable represents the presidential candidate the respondent voted for in the 2020 election in the form of a numerical variable.

### 2024-04-19 paper/Fake_News_vs_Fox_News.qmd
final changes, small grammar edits

@@
 The 2020 U.S.
-presidential election, between Republican President Donald Trump, and Democratic candidate Joe Biden, was one of the most intense in recent history.
-This was especially due to the large polarization in political opinion among Americans.
+presidential election, between Republican President Donald Trump and Democratic candidate Joe Biden, was one of the most intense in recent history.
+A key factor behind this can be attributed to the large polarization in political opinion among Americans.
 This was especially reflected in the media outlets favored by Americans, with Fox News being commonly known as the news network highly favored by Republicans, and Cable News Network (CNN) being commonly known as the Democrats' favorite.
@@
 He even handed out the "Fake News Award" through Twitter to several notable liberal media outlets, including CNN [@siddiqui2018trump].
-Democrats also have long-standing issues with the Republican news networks like Fox News.
+Democrats also have long-standing issues with Republican news networks like Fox News.
 For instance, Joe Biden has referred to Fox News as "one of the most destructive forces in the United States" [@stelter2022biden].
@@
 Consequently, it is important to explore whether US media networks have had significant influences on election outcomes.
-Understanding this could give a  good understanding of this relationship could enable voters to be more critical of the media they consume.
+A good understanding of this relationship could enable voters to be more critical of the media they consume.
 
@@
 
-The estimand of this paper is the probability of people voting Biden during the 2020 election based on news channel viewership.
+The estimand of this paper is the probability of people voting for Biden during the 2020 election based on news channel viewership.
 However, due to the difficulty of collecting data on millions of voters, this paper estimates the estimand using the logistic regression model trained using a sample from the CES dataset.
@@
 The findings indicate that watching media networks with specific political ideologies is associated with higher chances of voting for the candidate they prefer.
-This is most apparent in with CNN and Fox News, who are shown to exert heavy influence on voters identifying as "Independent" or "Other.".
-Watching local news over these national networks appears to have no significant effect on the probability of voting for Trump or Biden, as well.
+This is most apparent in with CNN and Fox News, who are shown to exert heavy influence on voters identifying as "Independent" or "Other." Additionally, this paper also studies the influence of watching national newscasts on voting outcomes compared to watching both national and local newscasts, finding no significant differences between the outcomes of the two.
 
@@
 The variable `votereg` represents whether the respondent is registered to vote using numerical numbers.
-This paper will only analyze respondents who are registered to vote and focus on the outcome of two candidates, Joe Biden representing the Democratic party and Donald Trump representing the Republican party.
+This paper will only analyze respondents who are registered to vote and focus on the outcome of two candidates, Joe Biden and Donald Trump.
 To analyze the observations of interest, I first limited the observations to the ones that responded "Yes" in `votereg`.
@@
 
-### Model justification
+## Model justification
 A positive relationship is expected between watching left-leaning (Democrat) media networks and voting for Biden, as well as a similar positive relationship between watching right-leaning (Republican) media networks and voting for Trump.

### 2024-04-19 paper/Fake_News_vs_Fox_News.qmd
delete one unwanted word
last change

@@
 Special thanks to my dear friends Luca Carnegie and Chaitanya Khamar for their love and support; this paper would not have been done so beautifully without your generous help and ideas.
-Special thanks for Rohan Alexander for his wonderful help and continual support.
+Special thanks to Rohan Alexander for his wonderful help and continual support.
 "
@@
 In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump).
-The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_{10}$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively.
+The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_{10}$) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively.
 Media use networks are being represented by the following predictor variables:  $\text{ABC}_i$, $\text{CBS}_i$, $\text{NBC}_i$, $\text{CNN}_i$, $\text{Fox\_News}_i$, $\text{MSNBC}_i$, $\text{PBS}_i$, $\text{Other}_i$.

### 2024-04-19 paper/Fake_News_vs_Fox_News.qmd
change graph title

@@
   scale_fill_manual(values = c("red", "blue")) +  # Specify colors for Biden and Trump
+  theme_minimal()+
   theme(plot.title = element_text(hjust = 0.5)) +
-  theme_minimal()+
   theme(legend.position="none")
